---
title: "AGBRESA Spatial Cognition 1"
author: "A Stahn"
date: "10/27/2021"
output: html_document
---
```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
# Prepare Script
## Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using Cowplot
```
## Print Session Info
```{r print R and package versions}
print(sessionInfo())
```
## Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report_white  <-  theme_pubr() + theme(
  axis.line = element_line(size = 0.5 / ggplot_factor_line,color="black"),
  axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
  axis.ticks.length = unit(0.2, "cm"), 
  text = element_text(size = 8 * ggplot_factor_font,
                      family="Helvetica",
                      colour="black"),
  axis.text.x=element_text(angle = 0, 
                           vjust = 0.5,
                           size = 8 * ggplot_factor_font,
                           family = "Helvetica",
                           colour = "black"), #face="bold"
  axis.text.y = element_text(angle = 0,
                            vjust=0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour="black"),
  axis.title.x = element_text(angle = 0,
                            vjust =0.5,
                            size= 8 * ggplot_factor_font,
                            family="Helvetica",
                            colour="black",
                            face="bold"),
  axis.title.y = element_text(angle = 90,
                            vjust = 0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour = "black",
                            face = "bold") # face = "bold" 
  )
```
## Load Data
```{r load data}
# Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], as.factor)

# SUT
df_sut <- read_excel("./Data/Data Spatial Cognition 1.xlsx", 
                     sheet = "Data SUT z")
df_sut[c(1:3)] <- lapply(df_sut[c(1:3)], as.factor)

# PTO
df_pto <- read_excel("./Data/Data Spatial Cognition 1.xlsx",
                     sheet = "Data PTO z")
df_pto[c(1:3)] <- lapply(df_pto[c(1:3)], as.factor)

# 4MTN
df_4mtn <- read_excel("./Data/Data Spatial Cognition 1.xlsx",
                      sheet = "Data 4MTN z")
df_4mtn[c(1:2)] <- lapply(df_4mtn[c(1:2)], as.factor)
df_4mtn <- as.data.frame(df_4mtn)

# NAVIS 2D
df_navis_2d <- read_excel("./Data/Data Spatial Cognition 1.xlsx",
                          sheet = "Data NAVIS 2D z")
df_navis_2d[c(1:3)] <- lapply(df_navis_2d[c(1:3)], as.factor)
```

# Definition of Helper Functions 
## Descriptive Functions
```{r functions for descriptive stats}
# Function to check data completion 
func_data_completion <- function(x) {x %>%
    group_by(variable) %>%
    dplyr::summarise(
    N = 24 * length( levels(time.f) ) * length( levels(cond.f) ),
    n = sum( !is.na(value) ),
                   Percent = n / N * 100
    )
}

# Function to compute descriptives, takes 'df_tmp_long'
func_desc_by_group_time_cond <- function(x) {x %>%
	group_by(variable, group_3, time.f, cond.f) %>%
	dplyr::summarise(MEAN = mean(value, na.rm=T),
	                 SE = sd(value,na.rm=T)/sqrt(length(value)) )
  
}

func_desc_by_group_time <- function(x) {x %>%
	group_by(variable, group_3, time.f) %>%
	dplyr::summarise(MEAN = mean(value, na.rm=T),
	                 SE = sd(value,na.rm=T)/sqrt(length(value)) )
}
```
## Plot Functions
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report_white +
    geom_line(position = pd) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4, 
                  position = pd) +
    geom_point(position = pd,
               shape = 21,
               size = 2) + #shape = 21, size = 1, fill = "white"
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10) +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 10))
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}

# Function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report_white +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none") +
    theme(legend.title = element_blank(),
          legend.text = element_text(size=8),
          axis.title.x = element_text(size = 10),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}

# Function for bar plots, takes 'desc*' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}
```
## Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML=T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

# Function for creating mixed model tables, takes 'dvList'
func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f); also requires 'func_mm_fac_with_bdc_adj_help'
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Helper function contrasts emmeans, takes 'dvList'; also requires 'func_mm_fac_with_bdc_adj_help'
func_contrasts_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac_with_bdc_adj <- function(dvList) {
  tmp <- func_contrasts_emm_fac_with_bdc_adj(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```
# Data Completion Check
```{r descriptive summaries for completed (missing) data}
# SUT
df_tmp <- df_sut
names(df_tmp)[names(df_tmp) == "sut_cond.f"] <- "cond.f"
df_tmp <- melt(df_tmp, id.vars=c("id", "time.f", "cond.f"))

missing_sut <- func_data_completion(df_tmp)

# 4MTN
df_tmp <- df_4mtn
df_tmp$cond.f <- as.factor( c( rep(1, nrow(df_tmp) ) ) )
df_tmp <- melt(df_tmp, id.vars=c("id", "time.f", "cond.f"))

missing_4mtn <- func_data_completion(df_tmp)

# PTO
df_tmp <- df_pto
names(df_tmp)[names(df_tmp) == "pto_cond.f"] <- "cond.f"
df_tmp <- melt(df_tmp, id.vars=c("id", "time.f", "cond.f"))
missing_pto <- func_data_completion(df_tmp)

# NAVIS 2D
df_tmp <- df_navis_2d
names(df_tmp)[names(df_tmp) == "navis_2d_cond.f"] <- "cond.f"
df_tmp <- melt(df_tmp, id.vars=c("id", "time.f", "cond.f"))
missing_navis_2d <- func_data_completion(df_tmp)

# Combine summary
spat_bat_1_summary <- bind_rows(missing_sut[1,], 
                              missing_4mtn[1,], 
                              missing_pto[1,], 
                              missing_navis_2d[1,]) 

spat_bat_1_summary$Task <- c("Spatial Updating Task", 
                           "Four Mountain Task",
                           "Point to Origin Task",
                           "Navigation Search Task 2D")

spat_bat_1_summary <- spat_bat_1_summary[c(5,2:4)]
colnames(spat_bat_1_summary)[2] <- "Expected (N)"
colnames(spat_bat_1_summary)[3] <- "Completed (N)"
colnames(spat_bat_1_summary)[4] <- "Completed (%)"
spat_bat_1_summary <- as.data.frame(spat_bat_1_summary)

datatable(spat_bat_1_summary) %>%
    formatRound(columns=c("Completed (%)"), digits = 1)
```
# Spatial Updating Task
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline SUT}
# Plot arithmetic means
df_tmp <- merge(df_demo, df_sut, by = c("id")) #add demo
names(df_tmp)[names(df_tmp) == "sut_cond.f"] <- "cond.f"

# Convert to long
df_tmp_long = reshape2::melt(df_tmp[-c(11)], id.vars = names(df_tmp)[c(1:10)])
                              
# Compute desc
desc <- func_desc_by_group_time_cond(df_tmp_long)

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency")
names(new_labels) <- c("rt_z","variable_pointing_error_z", "eff_z")

new_labels2 <- c("Static", "Short", "Long")
names(new_labels2) <- c("0", "25", "45")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(variable ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.sut_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z","variable_pointing_error_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.sut_desc <- p.sut_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.sut_desc <- p.sut_desc + theme(legend.key.size = unit(0.3, "cm"))
```

## Mixed Model Time x Group Interaction 
```{r mixed model for time x group SUT}
df_tmp <- df_sut
# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-3")
colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))], 
                                                     sep = "_")
df_tmp <- merge(df_tmp, df_tmp_pre[c(1, 4:7)], by = "id")

df_tmp <- subset(df_tmp, time.f !="BDC-3") # Drop baseline
df_tmp <- droplevels(df_tmp)
df_tmp <- merge(df_demo, df_tmp,by = c("id")) # Add demo
names(df_tmp)[names(df_tmp) == "sut_cond.f"] <- "cond.f"

# Select dep vars
dvList <- c("rt_z","variable_pointing_error_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Task Condition",
  "Time x Group",
  "Time x Task Condition",
  "Group x Task Condition",
  "Time x Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Precision", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_sut <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print table
datatable(tbl_mm_fac_aov_df_sut, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Comparing Groups at Each Time Point During Bed Rest
```{r contrasts for groups by time SUT}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3 * cond.f

# Define contrasts
contrast_type <- "pairwise"
factors <- c("cond.f", "time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) * 
  length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Precision", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Static", rep("", tmp_n_cond),
                                          "Short",rep("", tmp_n_cond),
                                          "Long",rep("", tmp_n_cond)),
                                        length(dvList) )

tbl_contr_emm_fac_df$Time <- rep ( c("HDT2", rep("", tmp_n_time),
                                     "HDT30", rep("", tmp_n_time),
                                     "HDT59", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Ttble for contrasts
tbl_contr_emm_fac_df_sut <- tbl_contr_emm_fac_df[c(9:11, 2, 8, 5:7)]

# print table
datatable(tbl_contr_emm_fac_df_sut, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot emmeans for groups by time SUT}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency")
names(new_labels) <- c("rt_z","variable_pointing_error_z", "eff_z")

new_labels2 <- c("Static", "Short Updating", "Long Updating")
names(new_labels2) <- c("0", "25", "45")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.sut_emmeans <- func_plot_line_facet(emm_fac %>%
                                        mutate(
                                          .id = fct_relevel(.id, "rt_z","variable_pointing_error_z", "eff_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.sut_emmeans <- p.sut_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.sut_emmeans <- p.sut_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group SUT}
# Drop recovery
df_tmp <- subset(df_tmp, time.f !="R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","variable_pointing_error_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Precision", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_sut_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print table
datatable(tbl_mm_fac_aov_df_sut_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```
## Contrasts for Comparing Groups
```{r contrasts for groups SUT}
# Define model for emmeans
model_emmeans <- ~ group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3 * cond.f

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c("cond.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * length(dvList) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Precision", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Static",rep("", tmp_n_cond),
                                          "Short",rep("", tmp_n_cond),
                                          "Long",rep("", tmp_n_cond)),
                                        length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_sut_main <- tbl_contr_emm_fac_df[c(8:9, 2, 7,4:6)]

# Print table
datatable(tbl_contr_emm_fac_sut_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Comparing Groups
```{r plot groups SUT}
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency")
names(new_labels) <- c("rt_z","variable_pointing_error_z", "eff_z")

new_labels2 <- c("Static", "Short", "Long")
names(new_labels2) <- c("0", "25", "45")

# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = cond.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = cond.f,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.sut_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                            mutate(.id = fct_relevel(.id, "rt_z","variable_pointing_error_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) 
# Adjust legend size
p.sut_emmeans_main <- p.sut_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
## Create Combined plot 
```{r plot combined SUT}
# Combine plot 
p.sut_comb <- plot_grid(p.sut_desc, p.sut_emmeans_main + rremove("x.text") +
                          theme(legend.key.size = unit(0.3, "cm")),
                        labels = c("a", "b"),
                        ncol = 2, nrow = 1,
                        rel_widths = c(2.2, 0.8))

# Adjust legend size
p.sut_comb <- p.sut_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 1/p.sut_comb.pdf",
    width = 30/2.54, 
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.sut_comb)
dev.off()
```
```{r, echo = FALSE, fig.width = 10, fig.height = 8, fig.cap="Figure SUT: (a) Time course of speed, precision, and efficiency before, during, and after bed rest. (b) Main effect of bed rest. Data are adjusted for baseline."}
print(p.sut_comb)
```

# Point to Origin Task
## Show Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline PTO}
# Plot arithmetic means
df_tmp <- merge(df_demo,df_pto, by = c("id")) #add demo
names(df_tmp)[names(df_tmp) == "pto_cond.f"] <- "cond.f"

# Convert to long
df_tmp_long = reshape2::melt(df_tmp, id.vars = names(df_tmp)[c(1:10)])
                              #arrange in 'full' long format (AND subset to specific time points) 
# Compute desc
desc <- func_desc_by_group_time_cond(df_tmp_long)

# Drop vars
desc <- subset(desc, variable != "rating_z" & variable != "direction_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency", "Distance Est.")
names(new_labels) <- c("rt_z","variable_pointing_error_z","eff_z", "dist_error_z")

new_labels2 <- c("Single", "Multiple", "Complex")
names(new_labels2) <- c("2", "3", "5")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(variable ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.pto_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z", "variable_pointing_error_z", "eff_z", "dist_error_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.pto_desc <- p.pto_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.pto_desc <- p.pto_desc + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model Time x Group Interaction 
```{r mixed model for time x group PTO}
df_tmp <- df_pto
# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-3")

colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))],
                                                     sep = "_")
df_tmp <- merge(df_tmp, df_tmp_pre[c(1,4:9)], by = "id")

df_tmp <- subset(df_tmp, time.f !="BDC-3") # Drop baseline
df_tmp <- droplevels(df_tmp)
df_tmp <- merge(df_demo, df_tmp,by =c("id")) # Add demo
names(df_tmp)[names(df_tmp) == "pto_cond.f"] <- "cond.f"

# Select dep vars
dvList <- c("rt_z","variable_pointing_error_z","eff_z", "dist_error_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Task Condition",
  "Time x Group",
  "Time x Task Condition",
  "Group x Task Condition",
  "Time x Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Precision", blanks, "Efficiency", blanks, "Distance Est.", blanks)
tbl_mm_fac_aov_df_pto <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print table
datatable(tbl_mm_fac_aov_df_pto, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", 'F'), digits = 1)
```
## Contrasts for Comparing Groups at Each Time Point
```{r emmeans for groups by time PTO}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3 * cond.f

# Define contrasts
contrast_type <- "pairwise"
factors <- c("cond.f", "time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) * 
  length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Precision", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs),
                                   "Distance Est.", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Single", rep("", tmp_n_cond),
                                          "Multiple",rep("", tmp_n_cond),
                                          "Complex",rep("", tmp_n_cond)),
                                        length(dvList) )

tbl_contr_emm_fac_df$Time <- rep ( c("HDT2", rep("", tmp_n_time),
                                     "HDT30", rep("", tmp_n_time),
                                     "HDT59", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

# Table for contrasts
tbl_contr_emm_fac_df_pto <- tbl_contr_emm_fac_df[c(9:11, 2, 8, 5:7)]
datatable(tbl_contr_emm_fac_df_pto, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot emmeans for groups by time PTO}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency","Distance Est.")
names(new_labels) <- c("rt_z","variable_pointing_error_z","eff_z", "dist_error_z")

new_labels2 <- c("Single", "Multiple", "Complex")
names(new_labels2) <- c("2", "3", "5")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.pto_emmeans <- func_plot_line_facet(emm_fac %>%
                                        mutate(
                                          .id = fct_relevel(.id, "rt_z", "variable_pointing_error_z", "eff_z", "dist_error_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.pto_emmeans <- p.pto_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.pto_emmeans <- p.pto_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group PTO}
# Drop recovery
df_tmp <- subset(df_tmp, time.f !="R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","variable_pointing_error_z","eff_z", "dist_error_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Precision", blanks, "Efficiency", blanks, "Distance Est.", blanks)
tbl_mm_fac_aov_df_pto_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print ANOVA table
datatable(tbl_mm_fac_aov_df_pto_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
##Contrasts for Comparing Groups
```{r contrasts for groups PTO}
# Define model for emmeans
model_emmeans <- ~ group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts 
# Define model for contrasts
model_emmeans <- ~ group_3 * cond.f

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c("cond.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Precision", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs),
                                   "Distance Est.", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Single",rep("", tmp_n_cond),
                                          "Multiple",rep("", tmp_n_cond),
                                          "Complex",rep("", tmp_n_cond)),
                                        length(dvList) )

# Table for contrasts
tbl_contr_emm_fac_pto_main <- tbl_contr_emm_fac_df[c(8:9, 2, 7,4:6)]

# Print Contrast table
datatable(tbl_contr_emm_fac_pto_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means to Compare Groups
```{r plot groups PTO}
# New facet label names for variable
new_labels <- c("Speed","Precision","Efficiency","Distance Est.", "Difficulty Rating")
names(new_labels) <- c("rt_z","variable_pointing_error_z","eff_z", "dist_error_z")

new_labels2 <- c("Single", "Multiple", "Complex")
names(new_labels2) <- c("2", "3", "5")

# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = cond.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = cond.f,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.pto_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                            mutate(.id = fct_relevel(.id, "rt_z", "variable_pointing_error_z", "eff_z", "dist_error_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) 

# Adjust legend size
p.pto_emmeans_main <- p.pto_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
### Plot Combined plot 
```{r create combined PTO}
# Combine plot
p.pto_comb <- plot_grid(p.pto_desc, p.pto_emmeans_main + rremove("x.text") + theme(legend.key.size = unit(0.3, "cm")), 
          labels = c("a", "b"),
          ncol = 2, nrow = 1,
          rel_widths = c(2.2, 0.8))

# Adjust legend size
p.pto_comb <- p.pto_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 1/p.pto_comb.pdf",
    width = 30/2.54,
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.pto_comb)
dev.off()
```
```{r, echo = FALSE, fig.width = 11, fig.height = 12, fig.cap="Figure PTO:(a) Time course of speed, precision, and efficiency before, during, and after bed rest. (b) Main effect of bed rest. Data are adjusted for baseline."}
print(p.pto_comb)
```
# Navigation Search Task 2D
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline NAVIS 2D}
# Plot arithmetic means
df_tmp <- merge(df_demo, df_navis_2d, by =c("id")) #add demo
names(df_tmp)[names(df_tmp) == "navis_2d_cond.f"] <- "cond.f"

# Convert to long
df_tmp_long = reshape2::melt(df_tmp, id.vars = names(df_tmp)[c(1:10)])
                              #arrange in 'full' long format (AND subset to specific time points) 
# Compute desc
desc <- func_desc_by_group_time_cond(df_tmp_long)

desc <- subset(desc, variable != "total_target_visits_z" & variable != "time_to_first_revisit_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Distance","Total Revisits")
names(new_labels) <- c("rt_z","acc_z","total_distance_z","total_revisits_z")

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(variable ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.navis_2d_desc <- func_plot_line_facet(desc %>%
                                          mutate(
                                            variable = fct_relevel(variable, "rt_z","acc_z","total_distance_z","total_revisits_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))
  
# Add zero line
p.navis_2d_desc <- p.navis_2d_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.navis_2d_desc <- p.navis_2d_desc + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model Time x Group Interaction 
```{r mixed model time x group NAVIS 2D}
df_tmp <- df_navis_2d
# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-3")
names(df_tmp_pre)
colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(4:ncol(df_tmp_pre))],
                                                     sep = "_")
df_tmp <- merge(df_tmp[c(1:9)], df_tmp_pre[c(1,4:9)], by = "id")

df_tmp <- subset(df_tmp, time.f !="BDC-3") # Drop baseline
df_tmp <- droplevels(df_tmp)
df_tmp <- merge(df_demo, df_tmp,by =c("id")) # Add demo
names(df_tmp)[names(df_tmp) == "navis_2d_cond.f"] <- "cond.f"

# Select dep vars
dvList <- c("rt_z","acc_z","total_distance_z","total_revisits_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Task Condition",
  "Time x Group",
  "Time x Task Condition",
  "Group x Task Condition",
  "Time x Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Distance", blanks, "Total Revisits",
              blanks)
tbl_mm_fac_aov_df_navis_2d <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print table
datatable(tbl_mm_fac_aov_df_navis_2d, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", 'F'), digits = 1)
```
##Contrasts for Comparing Groups at Each Time Point
```{r contrast for groups by time NAVIS 2D}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3 * cond.f

# Define contrasts
contrast_type <- "pairwise"
factors <- c("cond.f", "time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) * 
  length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

Variable <- c("Speed", blanks,"Accuracy", blanks, "Distance", blanks, "Total Revisits")

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Distance", rep("", tmp_n_dvs),
                                   "Total Revisits", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Day", rep("", tmp_n_cond),
                                          "Night",rep("", tmp_n_cond)),
                                        length(dvList) )

tbl_contr_emm_fac_df$Time <- rep ( c("HDT2", rep("", tmp_n_time),
                                     "HDT30", rep("", tmp_n_time),
                                     "HDT59", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_df_navis_2d <- tbl_contr_emm_fac_df[c(9:11, 2, 8, 5:7)]
datatable(tbl_contr_emm_fac_df_navis_2d, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot groups by time NAVIS 2D}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Distance","Total Revisits")
names(new_labels) <- c("rt_z","acc_z","total_distance_z","total_revisits_z")

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.navis_2d_emmeans <- func_plot_line_facet(emm_fac %>%
                                             mutate(
                                               .id = fct_relevel(.id, "rt_z","acc_z","total_distance_z","total_revisits_z"),
                                               group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.navis_2d_emmeans <- p.navis_2d_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.navis_2d_emmeans <- p.navis_2d_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group NAVIS 2D}
# Drop recovery
df_tmp <- subset(df_tmp, time.f !="R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","acc_z","total_distance_z","total_revisits_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Distance", blanks, "Total Revisits", blanks)
tbl_mm_fac_aov_df_navis_2d_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print ANOVA table
datatable(tbl_mm_fac_aov_df_navis_2d_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", 'F'), digits = 1)
```
## Compute Contrasts for Comparing Groups
```{r contrasts for groups NAVIS 2D}
# Define model for emmeans
model_emmeans <- ~ group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts 
# Define model for contrasts
model_emmeans <- ~ group_3 * cond.f

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c("cond.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Distance", rep("", tmp_n_dvs),
                                   "Total Revisits", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Day", rep("", tmp_n_cond),
                                          "Night",rep("", tmp_n_cond)),
                                        length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_navis_2d_main <- tbl_contr_emm_fac_df[c(8:9, 2, 7,4:6)]

# Print Contrast table
datatable(tbl_contr_emm_fac_navis_2d_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot groups NAVIS 2D}
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Distance","Total Revisits")
names(new_labels) <- c("rt_z","acc_z","total_distance_z","total_revisits_z")

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = cond.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = cond.f,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.navis_2d_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                                 mutate(
                                                   .id = fct_relevel(.id, "rt_z","acc_z","total_distance_z","total_revisits_z"),
                                                   group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.navis_2d_emmeans_main <- p.navis_2d_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
### Plot Combined plot 
```{r plot combined NAVIS 2D}
# Combine plot
p.navis_2d_comb <- plot_grid(p.navis_2d_desc, p.navis_2d_emmeans_main + rremove("x.text") + theme(legend.key.size = unit(0.3, "cm")),
          labels = c("a", "b"),
          ncol = 2, nrow = 1,
          rel_widths = c(2, 1))

# Adjust legend size
p.navis_2d_comb <- p.navis_2d_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 1/p.navis_2d_comb.pdf",
    width = 30/2.54,
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.navis_2d_comb)
dev.off()
```
```{r, echo = FALSE, fig.width = 9, fig.height = 9, fig.cap="Figure NAVIS 2D: (a) Time course of speed, accuracy, and distance before, during, and after bed rest. (b) Main effect of bed rest. Data are adjusted for baseline."}
print(p.navis_2d_comb)
```
# Four Mountains Task
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline 4MTN}
# Plot arithmetic means
df_tmp <- merge(df_demo, df_4mtn, by =c("id")) #add demo

# Convert to long
df_tmp_long = reshape2::melt(df_tmp, id.vars = names(df_tmp)[c(1:9)])

# Compute desc
desc <- func_desc_by_group_time(df_tmp_long)

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z","eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(~ variable,
                             switch = "y",
                             labeller = labeller_def) 

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)
# Draw plot
pd <- position_dodge(0.3)
p.4mtn_desc <- func_plot_line_facet(desc %>%
                                      mutate(
                                        variable = fct_relevel(variable, "rt_z","acc_z","eff_z"),
                                        group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.4mtn_desc <- p.4mtn_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")
```
## Mixed Model Time in Bed Rest x Group Interaction 
```{r mixed model for time x group 4MTN}
df_tmp <- df_4mtn
# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-3")
names(df_tmp_pre)
colnames(df_tmp_pre)[c(3:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(3:ncol(df_tmp_pre))], sep = "_")
df_tmp <- merge(df_tmp, df_tmp_pre[c(1,3:5)], by = "id")

df_tmp <- subset(df_tmp, time.f !="BDC-3") # Drop baseline
df_tmp <- droplevels(df_tmp)
df_tmp <- merge(df_demo, df_tmp,by =c("id")) # Add demo

# Select dep vars
dvList <- c("rt_z","acc_z","eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Time x Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Precision", blanks)
tbl_mm_fac_aov_df_4mtn <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print table
datatable(tbl_mm_fac_aov_df_4mtn, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", 'F'), digits = 1)
```
## Contrasts for Comparing Groups at Each Time Point
```{r constrasts for groups by time 4MTN}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c("time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f))  -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

Variable <- c("rt_z","acc_z","eff_z")

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Time <- rep ( c("HDT2", rep("", tmp_n_time),
                                     "HDT30", rep("", tmp_n_time),
                                     "HDT59", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_df_4mtn <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 3:6)]

datatable(tbl_contr_emm_fac_df_4mtn, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot groups by time 4MTN}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z","eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.4mtn_emmeans <- func_plot_line_facet(emm_fac %>%
                                         mutate(
                                           .id = fct_relevel(.id, "rt_z","acc_z","eff_z"),
                                           group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))
# Add zero line
p.4mtn_emmeans <- p.4mtn_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.4mtn_emmeans <- p.4mtn_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r  mixed model for main effect group  4MTN}
# Drop recovery
df_tmp <- subset(df_tmp, time.f !="R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","acc_z","eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_4mtn_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])

# Print ANOVA table
datatable(tbl_mm_fac_aov_df_4mtn_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", 'F'), digits = 1)
```
## Contrasts for Group Comparisons
```{r contrasts for groups 4MTN}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts 
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 1),
                                   "Accuracy", rep("", 1),
                                   "Efficiency", rep("", 1))

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_4mtn_main <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]

# Print Contrast table
datatable(tbl_contr_emm_fac_4mtn_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means fro Group Comparisons
```{r plot groups 4MTN}
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z","eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 
# Draw plot
pd <- position_dodge(1.5)
p.4mtn_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                             mutate(
                                               .id = fct_relevel(.id, "rt_z","acc_z","eff_z"),
                                               group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.4mtn_emmeans_main <- p.4mtn_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
## Plot Combined plot 
```{r plot combined 4MTN}
# Combine plot
p.4mtn_comb <- plot_grid(p.4mtn_desc, p.4mtn_emmeans_main + rremove("x.text") + theme(legend.key.size = unit(0.3, "cm")), 
          labels = c("a", "b"),
          ncol = 2, nrow = 1,
          rel_widths = c(2.2, 0.8))

# Adjust legend size
p.4mtn_comb <- p.4mtn_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 1/p.4mtn_comb.pdf",
    width = 30/2.54,
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.4mtn_comb)
dev.off()
```
```{r, echo = FALSE, fig.width = 10, fig.height = 3.5, fig.cap="Figure 4MTN: (a) Time course of speed, accuracy, and efficiency before, during, and after bed rest. (b) Main effect of bed rest. Data are adjusted for baseline."}
print(p.4mtn_comb)
```












