---
title: "AGBRESA Spatial Cognition 2"
author: "A Stahn"
date: "10/27/2021"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
# Prepare Script
## Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(nlme)
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using cowplot
```
## Print Session Info
```{r print R and package versions}
print(sessionInfo())
```
## Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report_white  <-  theme_pubr() + theme(
  axis.line = element_line(size = 0.5 / ggplot_factor_line,color="black"),
  axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
  axis.ticks.length = unit(0.2, "cm"), 
  text = element_text(size = 8 * ggplot_factor_font,
                      family="Helvetica",
                      colour="black"),
  axis.text.x=element_text(angle = 0, 
                           vjust = 0.5,
                           size = 8 * ggplot_factor_font,
                           family = "Helvetica",
                           colour = "black"), #face="bold"
  axis.text.y = element_text(angle = 0,
                            vjust=0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour="black"),
  axis.title.x = element_text(angle = 0,
                            vjust =0.5,
                            size= 8 * ggplot_factor_font,
                            family="Helvetica",
                            colour="black",
                            face="bold"),
  axis.title.y = element_text(angle = 90,
                            vjust = 0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour = "black",
                            face = "bold") # face = "bold" 
  )

#color
#p.sut_desc <- p.sut_desc + scale_color_brewer(palette="Paired",limits = c("cAG", "iAG", "CTRL"), labels = c("cAG", "iAG", "CTRL"))+scale_fill_brewer(palette="Paired",limits = c("cAG", "iAG", "CTRL"), labels = c("cAG", "iAG", "CTRL"))
#p.sut <- p.sut + scale_colour_manual(values = c("black", "black", "black"), labels = c("cAG", "iAG", "CTRL"))+scale_fill_brewer(palette="Paired",limits = c("cAG", "iAG", "CTRL"), labels = c("cAG", "iAG", "CTRL"))
#p.sut_main <- p.sut_main + scale_color_brewer(palette="Paired",limits = c("cAG", "iAG", "CTRL"), labels = c("cAG", "iAG", "CTRL"))+scale_fill_brewer(palette="Paired",limits = c("cAG", "iAG", "CTRL"), labels = c("cAG", "iAG", "CTRL"))

```
## Load Data
```{r load data}
#  Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], factor)

# Spatial Cognition performed before and after bed rest
# NAVIS VR
df_navis_vr <- read_excel("./Data/Data Spatial Cognition 1.xlsx", sheet = "Data NAVIS VR z")
df_navis_vr[c(1:3)] <- lapply(df_navis_vr[c(1:3)], as.factor)

# Spatial Cognition performed after bed rest
# SOT
df_sot <- read_excel("./Data/Data Spatial Cognition 2.xlsx", sheet = "Data SOT z")
df_sot[c(1:2)] <- lapply(df_sot[c(1:2)], as.factor)
df_sot[c(3:5)] <- lapply(df_sot[c(3:5)], as.numeric)

# Cognitive Mapping
df_cogmap <- read_excel("./Data/Data Spatial Cognition 2.xlsx", sheet = "Data Cognitive Mapping z")
df_cogmap[c(1:4)] <- lapply(df_cogmap[c(1:4)], as.factor)
df_cogmap[c(5:8)] <- lapply(df_cogmap[c(5:8)], as.numeric)
colnames(df_cogmap)[6] <- "acc_z"
colnames(df_cogmap)[7] <- "rt_z"
df_cogmap_agbresa <- subset(df_cogmap, group_2 != "CTRL_Amb" & group_2 != "R+180" )
df_cogmap_agbresa <- df_cogmap_agbresa[-c(2:5)]

# Water Maze
df_wm <- read_excel("./Data/Data Spatial Cognition 2.xlsx", sheet = "Data WM z")
df_wm[c(1:2)] <- lapply(df_wm[c(1:2)], as.factor)
df_wm[c(3:9)] <- lapply(df_wm[c(3:9)], as.numeric)
colnames(df_wm)[3] <- "rt_z"
colnames(df_wm)[4] <- "distance_z"
colnames(df_wm)[8] <- "heading_error_z"

# Plus Maze
df_pm <- read_excel("./Data/Data Spatial Cognition 2.xlsx", sheet = "Data PM z")
df_pm[c(1:2)] <- lapply(df_pm[c(1:2)], as.factor)
df_pm[c(3:ncol(df_pm))] <- lapply(df_pm[c(3:ncol(df_pm))], as.numeric)

# Navigation Strategy
df_navstrat <- read_excel("./Data/Data Spatial Cognition 2.xlsx", sheet = "Data Navstrat z")
df_navstrat[c(1:4)] <- lapply(df_navstrat[c(1:4)], as.factor)
df_navstrat[c(5:ncol(df_navstrat))] <- lapply(df_navstrat[c(5:ncol(df_navstrat))], as.numeric)

df_navstrat$direction <- factor(df_navstrat$direction,
levels = c("diff", "same"),
labels = c("Different", "Same"))
```
# Definition of Helper Functions 
## Descriptive Functions
```{r functions for descriptive stats}
# Function to check data completion 
func_data_completion <- function(data, ...) {
  
  if(!"time.f" %in% names(data)) {
    data$time.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  if(!"cond.f" %in% names(data)) {
    data$cond.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )  %>%
  
  group_by(variable) %>%
  dplyr::summarise(
      N = 24 * length( levels(time.f) ) * length( levels(cond.f) ),
      n = sum( !is.na(value) ),
      Percent = n / N * 100
      )
}

# Function to compute descriptives
func_desc <- function(data, ...) {
  df_tmp <- df_demo[ , !names(df_demo) %in% c("age","height", "weight")]
  data <- merge(df_tmp, data, by = "id") #add demo
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )
  groups <- enquos(...)
  
  result <- data %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      MEAN = mean(value, na.rm = T),
      SE = sd(value, na.rm = T) / sqrt(length(value) )
      )
  return(result)
}
```
## Plot Functions
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report_white +
    geom_line(position = pd) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4, 
                  position = pd) +
    geom_point(position = pd,
               shape = 21,
               size = 2) + # shape = 21, size = 1, fill = "white"
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10) +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 10))
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}

# Wrapper function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report_white +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none") +
    theme(legend.title = element_blank(),
          legend.text = element_text(size=8),
          axis.title.x = element_text(size = 10),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}

# Function for bar plots, takes 'desc' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}
```
## Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for appending bdc data as covariate
func_bdc_cov <- function(data, ...) {
  
  df_tmp <- subset(data, time.f != bdc)
  
  df_tmp_pre <- subset(data, time.f == bdc) %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .)) %>%
    select("id" | is.numeric)
  
  df_tmp <- merge(df_tmp_pre, df_tmp, by = "id")
  droplevels(df_tmp)
  
  df_tmp <- merge(df_demo, df_tmp,by  = c("id")) 
}

# nlme
# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_help_nlme <- function(dvList) {
  map(dvList, function(i) {
    f <- formula(paste(i, pred, sep = "~"))
    mm <- lme(fixed = f,
              random = ~ 1 | id,
              data = df_tmp)
    mm$call$fixed <- f
    mm}) %>% setNames(dvList)
}

# Helper functions for creating mixed model tables, takes 'dvList'
func_tbl_aov_nlme <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[2] <- "df1"
  names(tbl_mm_fac_aov)[3] <- "df2"
  names(tbl_mm_fac_aov)[4] <- "F"
  names(tbl_mm_fac_aov)[5] <- "P"
  tbl_mm_fac_aov[c(4)] <- round(tbl_mm_fac_aov[c(4)], digits = 2) # Round
  tbl_mm_fac_aov[c(5)] <- round(tbl_mm_fac_aov[c(5)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}


# Helper function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f)
func_emm_fac_nlme <- function(x) {
  mm_fac <- func_mm_fac_help_nlme(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Function for contrasts, requires 'func_mm_fac_help'
func_contrasts_emm_fac_nlme <- function(x) {
  mm_fac <- func_mm_fac_help_nlme(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust="none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer = T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Helper function contrasts emmeans, takes 'dvList', and requires func_contrasts_emm_fac_nlme
func_tbl_contr_emm_fac_nlme <- function(dvList) {
  tmp <- func_contrasts_emm_fac_nlme(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}

# lmer
# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML=T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

# Helper function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f)
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function for contrasts, requires 'func_mm_fac_help'
func_contrasts_emm_fac <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust="none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Function for contrast table; requires 'func_contrasts_emm_fac'
func_tbl_contr_emm_fac <- function(dvList) {
  tmp <- func_contrasts_emm_fac(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```
# Data Completion Check
```{r descriptive summaries for completed (missing) data}
# Spatial Cognition performed after
# SOT # Note: n=8 not collected, requires correction of func_data_completion
missing_sot <- func_data_completion(df_sot)

# Cognitive Mapping
missing_cogmap <- func_data_completion(df_cogmap_agbresa)

# Navigation Strategy
missing_navstrat <- func_data_completion(df_navstrat)
missing_navstrat$n <- missing_navstrat$n/12 # correct for additional conditions: 2 dir x 6 blocks
missing_navstrat$Percent <- missing_navstrat$Percent/12 # correct for additional conditions: 2 dir x 6 blocks

# virtual Water Maze
missing_wm <- func_data_completion(df_wm)

# PM
missing_pm <- func_data_completion(df_pm)

# Spatial Cognition performed before & after
# NAVIS VR
missing_navis_vr <- func_data_completion(df_navis_vr)

# Combine summary
spat_bat_2_summary <- bind_rows(
                              missing_sot[1,], 
                              missing_cogmap[1,],
                              missing_navstrat[1,],
                              missing_wm[1,],
                              missing_pm[1,],
                              missing_navis_vr[2,])  # note: Accuracy was 100%

spat_bat_2_summary$Task <- c("Spatial Orientation Task",
                           "Cognitive Mapping Task",
                           "Navigation Strategy Task",
                           "Water Maze Task",
                           "Plus Maze Task",
                           "Navigation Search Task VR")

spat_bat_2_summary <- spat_bat_2_summary[c(5,2:4)]
colnames(spat_bat_2_summary)[2] <- "Expected (N)"
colnames(spat_bat_2_summary)[3] <- "Completed (N)"
colnames(spat_bat_2_summary)[4] <- "Completed (%)"
spat_bat_2_summary <- as.data.frame(spat_bat_2_summary)
```
#### Table 1. Data collection summary Spatial Cognition 2.
```{r echo = FALSE}
datatable(spat_bat_2_summary) %>%
    formatRound(columns=c("Completed (%)"), digits = 1)

round(mean(spat_bat_2_summary$'Completed (%)'), 1)
```
# Spatial Orientation Task
## Mixed Model Comparing Groups
```{r mixed model SOT}
# Compute desc
desc <- func_desc(df_sot, group_3, variable)

# Mixed Models
# Add groups
df_tmp <- merge(df_demo, df_sot, by = "id") #add demo

# Select dep vars
dvList <- c("rt_z", "pointing_error_z", "score_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)
tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_sot <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(2:5)])
```
#### Table 2. Mixed Model Summary for Spatial Orientation Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_sot, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between groups SOT}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 2),
                                   "Accuracy", rep("", 2),
                                   "Efficiency", rep("", 2))

# Table for contrasts
tbl_contr_emm_fac_df_sot <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 3. Mixed Model Group Contrasts for Spatial Orientation Task.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_df_sot, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```

## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by group SOT}
# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) #requires mm_fac from nlme

# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "pointing_error_z","score_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 
# Draw plot
pd <- position_dodge(0.1)
p.sot_emmeans <- func_plot_bar_facet(emm_fac %>% 
                                       mutate(
                                         .id = fct_relevel(.id, "rt_z", "pointing_error_z", "score_z"),
                                         group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                         )
                                     ) 

# Adjust legend size
p.sot_emmeans <- p.sot_emmeans + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.sot_emmeans.pdf",
    width = 10/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.sot_emmeans)
dev.off()
```
#### Figure 1. Spatial Orientation Task: Effects of Bed Rest on Speed, Accuracy, and Efficiency on HDT59. Data are means and SE.
```{r, echo = FALSE, fig.width = 3, fig.height = 3, fig.cap = ""}
print(p.sot_emmeans)
```

# Virtual Water Maze
## Mixed Model Comparing Groups
```{r mixed model vWM}
# Compute desc
desc <- func_desc(df_wm, group_3, variable)

# Mixed Models
# Add groups
df_tmp <- merge(df_demo, df_wm, by = "id") #add demo

# Select dep vars
dvList <- c("rt_z", "distance_z", "heading_error_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)

tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Pathlength", blanks, "Heading Error", blanks)
tbl_mm_fac_aov_df_wm <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(2:5)])
```
#### Table 4. Mixed Model Summary for virtual Water Maze Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_wm, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Group Comparisons
```{r contrasts between groups vWM}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 2),
                                   "Pathlength", rep("", 2),
                                   "Heading Error", rep("", 2))

# Table for contrasts
tbl_contr_emm_fac_df_wm <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 5. Mixed Model Group Contrasts for virtual Water Maze Task.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_df_wm, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups vWM}
# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) # requires mm_fac from nlme

# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Pathlength","Heading Error")
names(new_labels) <- c("rt_z", "distance_z", "heading_error_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 
# Draw plot
pd <- position_dodge(0.1)
p.wm_emmeans <- func_plot_bar_facet(emm_fac %>% mutate(.id = fct_relevel(.id, "rt_z", "heading_error_z", "distance_z"),
                                                       group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                                       )
                                    ) 

# Adjust legend size
p.wm_emmeans <- p.wm_emmeans + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.wm_emmeans.pdf",
    width = 10/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.wm_emmeans)
dev.off()
```
#### Figure 2. Virtual Water Maze Task: Effects of bed rest on pathlength, heading error, and speed on HDT60. Data are means and SE.
```{r, echo = FALSE, fig.width = 3, fig.height = 3, fig.cap = ""}
print(p.wm_emmeans)
```

# Navigation Strategies Task
## Descriptive by block
```{r descriptive NavStrat}
# Compute desc
desc <- func_desc(df_navstrat, group_3, variable, block, direction)

# Drop vars
desc <- subset(desc, variable != "incorrects_z")

# Plot desc 
# Define aes for func_plot
tmpaes_plot <- aes(x = block, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = block,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "accuracy_z","eff_z")

new_labels2 <- c("Different Direction", "Same Direction")
names(new_labels2) <- c("Different", "Same")

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                         direction = new_labels2)

facet_grid_def <- facet_grid(variable ~ direction,
                             switch = "y",
                             labeller = labeller_def) 
# Draw plot
pd <- position_dodge(0.1)
p.navstrat_desc <- func_plot_line_facet(desc %>%
                                            mutate(variable = fct_relevel(variable, "rt_z", "accuracy_z", "eff_z"),
                                                   group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) 

# Adjust legend size
p.navstrat_desc <- p.navstrat_desc + theme(legend.key.size = unit(0.3, 'cm'))
```
## Mixed Model Comparing Groups
```{r mixed model NavStrat}
# Mixed Models
# Add groups
df_tmp <- merge(df_demo, df_navstrat, by = "id") #add demo

# Select dep vars
dvList <- c("rt_z", "accuracy_z", "eff_z")

# Select predictors
pred <- c("sex + age + block * group_3 * direction")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)

tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Block",
  "Group",
  "Direction",
  "Block x Group",
  "Block x Direction",
  "Group x Direction",
  "Block x Group x Direction"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_navstrat <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(3:5)])
```

#### Table 6. Mixed Model Summary for Navigation Strategies Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_navstrat, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between group NavStrat}
# Run Interaction Contrasts for Trends
mm_fac <- func_mm_fac_help_nlme(dvList)

contrasts_mm_fac <- lapply(mm_fac, function(mm_fac) 
  contrast(emmeans(mm_fac, ~ block * group_3 | direction),
           interaction = c("poly", "consec"),
           lmer.df = "satterthwaite",
           adjust="none") 
  )
# Add 95% CI
contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer = T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
rm(contrasts_mm_fac_)

# Clean
tmp <- contrasts_mm_fac_df
tmp[c(5:9)] <- round(tmp[c(5:9)], 1)
tmp[c(10)] <- round(tmp[c(10)], 2)
tmp[c(11)] <- round(tmp[c(11)], 3)
tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
tmp$CI <- gsub( ",", ", ", tmp$CI ) 
tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
colnames(tmp)[ncol(tmp)-2] <- "t"
colnames(tmp)[2] <- "Trend"
colnames(tmp)[3] <- "Contrast"
colnames(tmp)[4] <- "Direction"

tbl_contr_emm_fac_df <- tmp[c(2:4,12,7,10,11)]
  
# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 19),
                                   "Accuracy", rep("", 19),
                                   "Efficency", rep("", 19))

# Table for contrasts
tbl_contr_emm_fac_df_navstrat <- tbl_contr_emm_fac_df[c(8, 1:7)]
```
#### Table 7. Mixed Model Group Contrasts for Navigation Strategies Task.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_df_navstrat, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups and condition NavStrat}
# Run emmeans
model_emmeans <- ~ block * group_3 | direction
emm_fac <- func_emm_fac_nlme(dvList)

# Define aes for func_plot
tmpaes_plot <- aes(x = block, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = block,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# New facet label names for variable
new_labels <- c("Speed","Accuracy", "Efficiency")
names(new_labels) <- c("rt_z", "accuracy_z", "eff_z")

new_labels2 <- c("Same Direction","Different Direction")
names(new_labels2) <- c("Same", "Different")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   direction = new_labels2)

facet_grid_def <- facet_grid(.id ~ direction,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.4)
p.navstrat_emmeans <- func_plot_line_facet(emm_fac %>%
                                            mutate(.id = fct_relevel(.id, "rt_z", "accuracy_z", "eff_z"),
                                              group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                              )
                                           ) 

# Adjust legend size
p.navstrat_emmeans <- p.navstrat_emmeans + theme(legend.key.size = unit(0.3, 'cm'))

# Change axis title
p.navstrat_emmeans <- p.navstrat_emmeans + labs(y = "", x = "Block", size = 10) 

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.navstrat_emmeans.pdf",
    width = 8/2.54,
    height = 18/2.54,
    useDingbats = FALSE) #in cm
print(p.navstrat_emmeans)
dev.off()
```
#### Figure 3. Navigation Strategies Task: Effects of bed rest on speed, accuracy, and efficiency on HDT60. Data are means and SE.
```{r, echo = FALSE, fig.width = 6, fig.height = 9, fig.cap = ""}
print(p.navstrat_emmeans)
```

# Cognitive Mapping Task
## Mixed Model Comparing Groups
```{r mixed model CogMap}
# Compute desc
desc <- func_desc(df_cogmap_agbresa, group_3, variable)

# Mixed Models
# Add groups
df_tmp <- merge(df_demo, df_cogmap_agbresa, by = "id") #add demo

# Select dep vars
dvList <- c("rt_z", "acc_z", "eff_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)
tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_cogmap <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(3:5)])
```
#### Table 8. Mixed Model Summary for Cognitive Mapping Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_cogmap, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Group Comparisons
```{r contrasts between groups CogMap}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 2),
                                   "Accuracy", rep("", 2),
                                   "Efficiency", rep("", 2))

# Table for contrasts
tbl_contr_emm_fac_df_cogmap <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 9. Mixed Model Group Contrasts for Cognitive Mapping Task.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_df_cogmap, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by group CogMap}
# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) #requires mm_fac from nlme

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 
# Draw plot
pd <- position_dodge(0.1)
p.cogmap_emmeans <- func_plot_bar_facet(emm_fac %>%
                                          mutate(.id = fct_relevel(.id, "rt_z", "acc_z", "eff_z"),
                                                        group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                                        )
                                                 ) 

# Adjust legend size
p.cogmap_emmeans <- p.cogmap_emmeans + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.cogmap_emmeans.pdf",
    width = 10/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.cogmap_emmeans)
dev.off()
```
#### Figure 4. Cognitive Mapping Task: Effect of bed rest on speed, accuracy, and efficiency on HDT59. Data are means and SE.
```{r, echo = FALSE, fig.width = 3, fig.height = 3, fig.cap = ""}
print(p.cogmap_emmeans)
```

# Plus Maze Task
## Mixed Model Comparing Groups
```{r mixed model PM}
# Compute desc
desc <- func_desc(df_pm, group_3, variable)

# Mixed Models
# Add groups
df_tmp <- merge(df_demo, df_pm, by = "id") #add demo

# Select dep vars
dvList <- c("place_cor_z", "response_cor_z", "switch_cor_z", "reversal_cor_z", "switchtoplace_cor_z", "switchtoresponse_cor_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)
tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9, 13, 17, 21),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Place Strategy", blanks,"Response Strategy", blanks, "Switch", blanks, "Reversal", blanks, "S2P", blanks, "S2R", blanks)
tbl_mm_fac_aov_df_pm <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(2:5)])
```
#### Table 10. Mixed Model Summary for virtual Plus Maze Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_pm, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Group Comparisons
```{r contrasts between groups PM}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Place Strategy", rep("", 2),
                                   "Response Strategy", rep("", 2),
                                   "Switch", rep("", 2),
                                   "Reversal", rep("", 2),
                                   "S2P", rep("", 2),
                                   "S2R", rep("", 2))

# Table for contrasts
tbl_contr_emm_fac_df_sot <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 11. Mixed Model Group Contrasts for virtual Plus Maze Task.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_df_sot, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by group PM}
# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) #requires mm_fac from nlme

# New facet label names for variable
new_labels <- c("Place Strategy", "Response Strategy", "Switch", "Reversal", "S2P", "S2R")
names(new_labels) <- c("place_cor_z", "response_cor_z", "switch_cor_z", "reversal_cor_z", "switchtoplace_cor_z", "switchtoresponse_cor_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             labeller = labeller_def,
                             ncol = 2) 

facet_grid_def <- facet_wrap(~ .id,
                             labeller = labeller_def,
                             nrow = 2) 

# Draw plot
pd <- position_dodge(0.1)
p.pm_emmeans <- func_plot_bar_facet(emm_fac %>% 
                                      mutate(.id = fct_relevel(.id, "place_cor_z", "response_cor_z", "switch_cor_z", "reversal_cor_z", "switchtoplace_cor_z", "switchtoresponse_cor_z"),
                                         group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                         )
                                    ) 

# Adjust legend size
p.pm_emmeans <- p.pm_emmeans + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.pm_emmeans.pdf",
    width = 10/2.54,
    height = 6/2.54,
    useDingbats = FALSE) #in cm
print(p.pm_emmeans)
dev.off()
```
#### Figure 5. Plus Maze Task: Effect of bed rest on lace Strategy, Response Strategy, Switch, Reversal, Switch to Place (S2P), Switch to Response (S2R) on R+1. Data are means and SE.
```{r, echo = FALSE, fig.width = 5, fig.height = 6, fig.cap = ""}
print(p.pm_emmeans)
```

# Navigation Search VR
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline NAVIS VR}
# Compute desc
desc <- func_desc(df_navis_vr, group_3, cond.f, time.f, variable)

# Drop vars
desc <- subset(desc, variable != "acc_z" & variable != "time_to_first_revisit_z" & variable != "eff_acc_z" & variable != "eff_totdistance_z" & variable != "eff_totrevists_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Distance","Revisits")
names(new_labels) <- c("rt_z","total_distance_z","total_revisits_z")

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(variable ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.navis_vr_desc <- func_plot_line_facet(desc %>%
                                          mutate(variable = fct_relevel(variable, "rt_z", "total_distance_z", "total_revisits_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                            )
                                        ) +
  geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.navis_vr_desc <- p.navis_vr_desc + theme(legend.key.size = unit(0.3, 'cm'))
```
## Mixed Model for Group x Time Interaction
```{r mixed model NAVIS VR}
# Mixed Models
# Add baseline as cov
bdc <- "BDC-6"
df_tmp <-  func_bdc_cov(df_navis_vr)

# Select dep vars
dvList <- c("rt_z","total_distance_z","total_revisits_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f", "* group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Task Condition",
  "Time x Group",
  "Time x Task Condition",
  "Group x Task Condition",
  "Time x Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks, "Distance", blanks, "Revisits", blanks)
tbl_mm_fac_aov_df_navis_vr <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 12. Mixed Model Summary for Navigation Search Task VR.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_navis_vr, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Group Comparisons at Each Timepoint
```{r contrasts between groups by time NAVIS VR}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3 * cond.f

# Define contrasts
contrast_type <- "pairwise"
factors <- c("cond.f", "time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) * 
  length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

Variable <- c("Speed", blanks, "Distance", blanks, "Revisits", blanks)

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Distance", rep("", tmp_n_dvs),
                                   "Revisits", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Day", rep("", tmp_n_cond),
                                          "Night",rep("", tmp_n_cond)),
                                        length(dvList) )

tbl_contr_emm_fac_df$Time <- rep ( c("R+1", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))
```
#### Table 13. Mixed Model Group Contrasts for Navigation Search Task VR.
```{r echo = FALSE}
# Table for contrasts
tbl_contr_emm_fac_df_navis_vr <- tbl_contr_emm_fac_df[c(9:11, 2, 8, 5:7)]
datatable(tbl_contr_emm_fac_df_navis_vr, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```
## Plot Estimated Marignal Means for Group x Time Comparisons
```{r plot emmeans by group and time NAVIS VR}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed", "Distance", "Revisits")
names(new_labels) <- dvList

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.navis_vr_emmeans <- func_plot_line_facet(emm_fac %>% 
                                             mutate(.id = fct_relevel(.id, "rt_z", "total_distance_z", "total_revisits_z"),
                                               group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) +
  geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.navis_vr_emmeans <- p.navis_vr_emmeans + theme(legend.key.size = unit(0.3, 'cm'))
```
## Mixed Model assessing Main Effect of Bed Rest
```{r compute mixed model for main effect NAVIS VR}
# Drop recovery
df_tmp <- subset(df_tmp, time.f !="R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","total_distance_z","total_revisits_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * cond.f", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks, "Distance", blanks, "Revisits", blanks)
tbl_mm_fac_aov_df_navis_vr_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 14. Mixed Model Summary for Navigation Search Task VR.
```{r echo = FALSE}
# Print ANOVA table
datatable(tbl_mm_fac_aov_df_navis_vr_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P"), digits = 3) %>%
  formatRound(columns=c("df2", "F"), digits = 1)
```
## Contrasts for Group Comparisons
```{r contrasts between groups main effect NAVIS VR}
# Define model for emmeans
model_emmeans <- ~ group_3 * cond.f

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts 
# Define model for contrasts
model_emmeans <- ~ group_3 * cond.f

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c("cond.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * length(levels(tbl_contr_emm_fac_df$cond.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Distance", rep("", tmp_n_dvs),
                                   "Revisits", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Day", rep("", tmp_n_cond),
                                          "Night",rep("", tmp_n_cond)),
                                        length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_navis_vr_main <- tbl_contr_emm_fac_df[c(8:9, 2, 7,4:6)]
```
#### Table 15. Mixed Model Group Contrasts for Navigation Search task VR. Data are adjusted for baseline.
```{r echo = FALSE}
# Print Contrast table
datatable(tbl_contr_emm_fac_navis_vr_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("t"), digits = 2)
```
## Compute and Plot Estimated Marignal Means to Compare Groups
```{r plot emmeans by group NAVIS VR}
# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = cond.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = cond.f,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Distance","Revisits")
names(new_labels) <- c("rt_z","total_distance_z","total_revisits_z")

new_labels2 <- c("Day", "Night")
names(new_labels2) <- c("Day", "Night")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   cond.f = new_labels2)

facet_grid_def <- facet_grid(.id ~ cond.f,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.navis_vr_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                                 mutate(.id = fct_relevel(.id, "rt_z", "total_distance_z", "total_revisits_z"),
                                                   group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")
                                                   )
                                               )


# Adjust legend size
p.navis_vr_emmeans_main <- p.navis_vr_emmeans_main + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.navis_vr_emmeans_main.pdf",
    width = 4/2.54,
    height = 18/2.54,
    useDingbats = FALSE) #in cm
print(p.navis_vr_emmeans_main)
dev.off()
```
#### Figure 6. Navigation Search Task VR: Effect of bed rest on speed, distance traveled, and total speed on R+1. Data are means and SE adjusted for baseline.
```{r, echo = FALSE, fig.width = 3, fig.height = 8, fig.cap = ""}
print(p.navis_vr_emmeans_main)
```

## Create Combined plot 
```{r combined plot NAVIS VR}
# Combine plot
p.navis_vr_comb <- plot_grid(p.navis_vr_desc, p.navis_vr_emmeans_main + rremove("x.text") + theme(legend.key.size = unit(0.3, 'cm')),
          labels = c("a", "b"),
          ncol = 2, nrow = 1,
          rel_widths = c(2, 1))

p.navis_vr_comb <- p.navis_vr_comb + theme(legend.key.size = unit(0.3, 'cm'))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 2/p.navis_vr_comb.pdf",
    width = 30/2.54,
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.navis_vr_comb)
dev.off()
```
```{r, echo = FALSE, fig.width = 8, fig.height = 8, fig.cap = "Figure NAVIS VR: Effect of bed rest on speed, distance traveled, and total speed on R+1."}
print(p.navis_vr_comb)
```
