---
title: "Appendix Final Report HyperCampus Cognition"
#author: "A Stahn"
#date: "10/27/2021"
#output:
 # officedown::rdocx_document
  #word_document:
    #number_sections: TRUE
    #fig_caption: TRUE
  #bookdown::html_document2:
  #number_sections: TRUE
  #fig_caption: TRUE
  #always_allow_html: true
output:  
  officedown::rdocx_document:
    tables:
      table.align: "center"
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
        text.align: "left"
    plots:
      align: left
      caption:
        sep: '. '
---
```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, dpi = 300, echo = FALSE)
```
##Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(nlme)
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using cowplot
library(officedown)
library(officer)
library(flextable)
```
##Load Data
```{r load data}
# Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], factor)

# Cognition
df_cognition <- read_excel("./Data/Data Cognition.xlsx", 
                     sheet = "Data Cognition")

# Convert var types
df_cognition[c(1:3)] <- lapply(df_cognition[c(1:3)], as.factor)

# Unify col names
names(df_cognition)[names(df_cognition) == "PVT_Accuracy"] <- "PVT_pCorr"
names(df_cognition)[names(df_cognition) == "PVT_Slowness"] <- "PVT_AvRT"
names(df_cognition)[names(df_cognition) == "BART_RiskScoreP"] <- "BART_pCorr"
names(df_cognition)[names(df_cognition) == "MP_Accuracy"] <- "MP_pCorr"
names(df_cognition)[names(df_cognition) == "LOT_Accuracy"] <- "LOT_pCorr"
names(df_cognition)[names(df_cognition) == "NBCK_Av_pCorr"] <- "NBCK_pCorr"

# Add 'z'
colnames(df_cognition)[c(4:ncol(df_cognition))] <- paste(colnames(df_cognition[c(4:ncol(df_cognition))]), "z", sep = "_")

# relabel Battery numbers
#df_cognition$time.n <- plyr::revalue(df_cognition$time.f, c("BDC-9" = "01", "BDC-7" = "02", "BDC-6" = "03", "HDT1" = "04", "HDT3" = "05", "HDT5" = "06", "HDT14" = "07", "HDT28" = "08", "HDT42" = "09", "HDT57" = "10", "R+1" = "11", "R+5" = "12", "R+12" = "13"))

#df_cognition <- df_cognition[c(1:3, 34, 4:33)]
#df_cognition$time.n <- as.character((df_cognition$time.n))
#df_cognition$time.n <- as.numeric((df_cognition$time.n))
```
##Descriptive Functions
```{r functions for descriptive stats}
# Function to check data completion 
func_data_completion <- function(data, ...) {
  
  if(!"time.f" %in% names(data)) {
    data$time.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  if(!"cond.f" %in% names(data)) {
    data$cond.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )  %>%
  
  group_by(variable) %>%
  dplyr::summarise(
      N = 24 * length( levels(time.f) ) * length( levels(cond.f) ),
      n = sum( !is.na(value) ),
      Percent = n / N * 100
      )
}

# Function to compute descriptives
func_desc <- function(data, ...) {
  df_tmp <- df_demo[ , !names(df_demo) %in% c("age","height", "weight")]
  data <- merge(df_tmp, data, by = "id") #add demo
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )
  groups <- enquos(...)
  
  result <- data %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      MEAN = mean(value, na.rm = T),
      SE = sd(value, na.rm = T) / sqrt(length(value) )
      )
  return(result)
}

func_bdc_correction <- function(data, ...) {

  df_tmp <- data %>%
    subset(time.f == "BDC-6" | time.f == "BDC-7" |time.f == "BDC-9") %>%
    group_by(group_3, variable) %>%
    dplyr::summarise(
      mean_bdc_by_group = mean(MEAN, na.rm = T)
      )
  
  df_tmp <- merge(df_tmp, data, by = c("group_3", "variable") )
  df_tmp %>%
    mutate(MEAN_corr = case_when(time.f == "BDC-6" | time.f == "BDC-7" | time.f == "BDC-9" ~
                              MEAN-mean_bdc_by_group,
                            TRUE ~ MEAN)) %>%
    select( c(!mean_bdc_by_group & !MEAN) ) %>%
    dplyr::rename(MEAN = MEAN_corr)
}
```
##Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for appending bdc data as covariate
func_bdc_cov <- function(data, ...) {
  
  df_tmp <- subset(data, time.n > bdc )
  
  df_tmp_pre <- subset(data, time.n < (bdc+1) ) %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .)) %>%
    select("id" | is.numeric)

  df_tmp <- merge(df_tmp_pre[-c(2)], df_tmp, by = c("id") )
  droplevels(df_tmp)
 
  df_tmp <- merge(df_demo, df_tmp, by  = c("id")) 
}

func_bdc_cov_multi_sep <- function(data, ...) {
  df_tmp <- subset(data[-c(2)], time.n > bdc )
  df_tmp_pre <- subset(data, time.n < (bdc+1) )
  df_tmp_pre <- df_tmp_pre[,!grepl("time.n", colnames(df_tmp_pre))] 
  df_tmp_pre <- 
    reshape2::melt( df_tmp_pre, 
                              id.vars = names( Filter(is.factor, df_tmp_pre) )
                              ) %>%
    group_by(id, variable) %>%
    dplyr::summarise(
      mean_bdc = mean(value, na.rm = T) 
    )
  df_tmp_pre <- reshape2::dcast( df_tmp_pre, id ~ variable, value.var = "mean_bdc") %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .))
  df_tmp <- merge(df_tmp_pre, df_tmp, by = c("id") )
  droplevels(df_tmp)
  df_tmp <- merge(df_demo[c(1,3,5:6)], df_tmp, by  = c("id"))
  }

# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML = T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

# Function for creating mixed model tables, takes 'dvList'
func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f); also requires 'func_mm_fac_with_bdc_adj_help'
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Helper function contrasts emmeans, takes 'dvList'; also requires 'func_mm_fac_with_bdc_adj_help'
func_contrasts_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "fdr"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac_with_bdc_adj <- function(dvList) {
  tmp <- func_contrasts_emm_fac_with_bdc_adj(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```
#Functions tables
```{r functions for flextable}
theme_tableflex_report <- function(x, ...) {
  std_b <- fp_border(width = 1.5, color = "black")
  thin_b <- fp_border(width = 0.5, color = "black")
    x <- border_remove(x)
    x <- hline(x, border = thin_b, part = "all")
    x <- hline_top(x, border = std_b, part = "header")
    x <- hline_bottom(x, border = std_b, part = "header")
    x <- hline_bottom(x, border = std_b, part = "body")
    x <- bold(x = x, bold = TRUE, part = "header")
    x <- align_text_col(x, align = "left", header = TRUE)
    x <- align_nottext_col(x, align = "center", header = TRUE)
    fix_border_issues(x)
    autofit(x)
}

set_flextable_defaults(
  font.size = 10,
  font.family = "Times New Roman",
  theme_fun = theme_tableflex_report)
  #padding = 6)
  #background.color = "#EFEFEF")
```
#Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report <- function(base_size = 8) {
  theme_pubr() + #%+replace%
    theme(
      plot.margin = margin(0, 0, 0, 0, "cm"),
      text = element_text(size = 8,
                      colour="black"), #family="Helvetica"
      # axes
      axis.title = element_text(size = 8, face = "bold"), #vjust = 0.5
      axis.text = element_text(size = 8), #angle = 0
      axis.line = element_line(size = 0.5 / ggplot_factor_line, color="black"),
      axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
      axis.ticks.length = unit(0.2, "cm"), 
      # legend
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.title = element_blank(),
      legend.text = element_text(size = 8),
      axis.title.x = element_text(size = 8),
      # facetting
      strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5),
                                          #linetype = "solid"),
          strip.text = element_text(size = 8,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(1.5, "lines")
    )
}

```
#Functions Plotting
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report() +
    geom_line(position = pd,
              size = 0.3) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4,
                  size = 0.3,
                  position = pd) +
    geom_point(position = pd,
               #shape = 21,
               size = 2) +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10)
    #scale_shape_manual(values=c(3, 16, 17))+
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def
}


# Function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report() +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none")
}

# Function for bar plots, takes 'desc*' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def
}
```
# Data Completion Check
```{r descriptive summaries for completed (missing) data}
# Cognition
missing_cognition <- func_data_completion(df_cognition)
# Rename column
names(missing_cognition)[names(missing_cognition) == "variable"] <- "Variable"
names(missing_cognition)[names(missing_cognition) == "N"] <- "Expected (N)"
names(missing_cognition)[names(missing_cognition) == "n"] <- "Completed (N)"
names(missing_cognition)[names(missing_cognition) == "Percent"] <- "Completed (%)"
missing_cognition$Variable  <- gsub("_AvRT_z", "", missing_cognition$Variable )
missing_cognition$Variable  <- gsub("_pCorr_z ", "", missing_cognition$Variable )
missing_cognition$Variable  <- gsub("_Eff_z ", "", missing_cognition$Variable )
```
```{r tab.cap = "Data collection summary Cognition.", tab.cap.style = "Table Caption", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
cognition_summary <- missing_cognition %>% flextable() %>% autofit() %>% 
  colformat_double(j = c("Completed (%)"), digits = 1) 
# Print
cognition_summary
```
#Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline}
# Plot arithmetic means
# Compute desc
desc_all <- func_desc(df_cognition, group_3, time.f, variable)

# Shift mean within groups to reflect a pre-HDT baseline performance of 0 (zero) (To reflect the analytical approach (adjusting for baseline performance).
desc_all <- func_bdc_correction(desc_all)

# Plot 
# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define positioning
pd <- position_dodge(0.3)

# Speed
# Select
desc <- dplyr::filter(desc_all, grepl("AvR", variable))
desc <- droplevels(desc)
# New facet label names for variable
new_labels <- c("MP Speed", "VOLT", "NBACK", "AM", "LOT", "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_AvRT_z", "VOLT_AvRT_z", "NBCK_AvRT_z", "AM_AvRT_z", "LOT_AvRT_z", "ERT_AvRT_z", "MRT_AvRT_z", "DSST_AvRT_z", "BART_AvRT_z", "PVT_AvRT_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels)

facet_grid_def <- facet_wrap(~ variable,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw plot
p.cognition_desc_AvRT <- func_plot_line_facet(desc %>%
                                                 mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")) %>%
  mutate(time.f = fct_relevel(time.f, "BDC-9", "BDC-7", "BDC-6", "HDT1", "HDT3", "HDT5","HDT14", "HDT28", "HDT42", "HDT57", "R+1", "R+5", "R+12"))) +
  geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.cognition_desc_AvRT <- p.cognition_desc_AvRT + theme(legend.key.size = unit(0.3, "cm"))

# Accuracy
# Select
desc <- dplyr::filter(desc_all, grepl("pCorr",variable))
desc <- droplevels(desc)

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_pCorr_z", "VOLT_pCorr_z", "NBCK_Av_pCorr_z", "AM_pCorr_z", "LOT_pCorr_z", "ERT_pCorr_z", "MRT_pCorr_z", "DSST_pCorr_z", "BART_pCorr_z", "PVT_pCorr_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels)

facet_grid_def <- facet_wrap(~ variable,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw plot
p.cognition_desc_pCorr <- func_plot_line_facet(desc %>%
                                                 mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")) %>%
  mutate(time.f = fct_relevel(time.f, "BDC-9", "BDC-7", "BDC-6", "HDT1", "HDT3", "HDT5","HDT14", "HDT28", "HDT42", "HDT57", "R+1", "R+5", "R+12"))) +
  geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.cognition_desc_pCorr <- p.cognition_desc_pCorr + theme(legend.key.size = unit(0.3, "cm"))

# Efficiency
# Select
desc <- dplyr::filter(desc_all, grepl("Eff",variable))
desc <- subset(desc, variable != "BART_Eff_z")
desc <- droplevels(desc)

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST" , "PVT")
names(new_labels) <- c("MP_Eff_z", "VOLT_Eff_z", "NBCK_Eff_z", "AM_Eff_z", "LOT_Eff_z", "ERT_Eff_z", "MRT_Eff_z", "DSST_Eff_z", "PVT_Eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels)

facet_grid_def <- facet_wrap(~ variable,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw plot
p.cognition_desc_eff <- func_plot_line_facet(desc %>%
                                                 mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")) %>%
  mutate(time.f = fct_relevel(time.f, "BDC-9", "BDC-7", "BDC-6", "HDT1", "HDT3", "HDT5","HDT14", "HDT28", "HDT42", "HDT57", "R+1", "R+5", "R+12"))) +
  geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.cognition_desc_eff <- p.cognition_desc_eff + theme(legend.key.size = unit(0.3, "cm"))
```
##Mixed Model Time x Group Interaction 
```{r mixed model for time x group Cognition}
# Create baseline data
# relabel time.f
df_cognition$time.n <- plyr::revalue(df_cognition$time.f, c("BDC-9" = "01", "BDC-7" = "02", "BDC-6" = "03", "HDT1" = "04", "HDT3" = "05", "HDT5" = "06", "HDT14" = "07", "HDT28" = "08", "HDT42" = "09", "HDT57" = "10", "R+1" = "11", "R+5" = "12", "R+12" = "13"))
df_cognition <- df_cognition[c(1:3, 34, 4:33)]
df_cognition$time.n <- as.character((df_cognition$time.n))
df_cognition$time.n <- as.numeric((df_cognition$time.n))

# Define BDC sessions (number indicates last bdc sessions based on time.n)
bdc <- 3

# Create df with bdc as covariate
df_tmp <- func_bdc_cov_multi_sep(df_cognition, id)

# Select dep vars
dvList <- colnames(df_tmp)[c(37:66)]

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- lapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simply = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Sort by variable
tbl_mm_fac_aov_df_AvRT <- dplyr::filter(tbl_mm_fac_aov_df, grepl("AvR", X1))
tbl_mm_fac_aov_df_pCorr <- dplyr::filter(tbl_mm_fac_aov_df, grepl("pCorr", X1))
tbl_mm_fac_aov_df_eff <- dplyr::filter(tbl_mm_fac_aov_df, grepl("Eff", X1))

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Time x Group"),
                 length(dvList)/3)
}

# Create parameters
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / ( length(dvList) / 3) - 1)
Variable <-  c("MP", blanks,"VOLT", blanks, "NBCK", blanks, "AM", blanks, "LOT", blanks, "ERT", blanks, "MRT", blanks, "DSST", blanks, "BART", blanks, "PVT", blanks)

# Add to parameters to tables
tbl_mm_fac_aov_df_AvRT <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_AvRT[c(4:7)])
tbl_mm_fac_aov_df_pCorr <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_pCorr[c(4:7)])
tbl_mm_fac_aov_df_eff <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_eff[c(4:7)])

# Drop BART from Eff
tbl_mm_fac_aov_df_eff <- tbl_mm_fac_aov_df_eff[-c( 49:54),]
```
```{r tab.cap = " Mixed Model Summary for Cognition Speed.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_AvRT <- tbl_mm_fac_aov_df_AvRT %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_AvRT
```
```{r tab.cap = " Mixed Model Summary for Cognition Accuracy.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_pCorr <- tbl_mm_fac_aov_df_pCorr %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_pCorr
```
```{r tab.cap = " Mixed Model Summary for Cognition Efficiency.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_eff <- tbl_mm_fac_aov_df_eff %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_eff
```
##Contrasts for Comparing Groups at Each Time Point During Bed Rest
```{r contrasts for groups by time}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c("time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList %>% 
                                       mutate(time.f = fct_relevel(time.f, "HDT1", "HDT3", "HDT5", "HDT14", "HDT28", "HDT42","HDT57", "R+1", "R+5", "R+12"))) 

# Add variables
# AvRT
tbl_contr_emm_fac_df_AvRT <- dplyr::filter(tbl_contr_emm_fac_df, grepl("AvR", .id))
#tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT[c(8:9, 2, 7, 4:6)]

# pCorr
tbl_contr_emm_fac_df_pCorr <- dplyr::filter(tbl_contr_emm_fac_df, grepl("pCorr", .id))
#tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr[c(8:9, 2, 7, 4:6)]

# Eff
tbl_contr_emm_fac_df_eff <- dplyr::filter(tbl_contr_emm_fac_df, grepl("Eff", .id))
#tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[c(8:9, 2, 7, 4:6)]

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) -1

tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

Variable <- c("MP", rep("", tmp_n_dvs),
                                   "VOLT", rep("", tmp_n_dvs),
                                   "NBCK", rep("", tmp_n_dvs),
                                   "AM", rep("", tmp_n_dvs),
                                   "LOT", rep("", tmp_n_dvs),
                                   "ERT", rep("", tmp_n_dvs),
                                   "MRT", rep("", tmp_n_dvs),
                                   "DSST", rep("", tmp_n_dvs),
                                   "BART", rep("", tmp_n_dvs),
                                   "PVT", rep("", tmp_n_dvs))

Time <- rep ( c("HDT1", rep("", tmp_n_time),
                                     "HDT3", rep("", tmp_n_time),
                                     "HDT5", rep("", tmp_n_time),
                                     "HDT14", rep("", tmp_n_time),
                                     "HDT28", rep("", tmp_n_time),
                                     "HDT42", rep("", tmp_n_time),
                                     "HDT57", rep("", tmp_n_time),
                                     "R+1", rep("", tmp_n_time),
                                     "R+5", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList)/3 )

# Add to parameters to tables
tbl_contr_emm_fac_df_AvRT <- cbind(Variable, Time, tbl_contr_emm_fac_df_AvRT[c(2, 7, 4:6)])

tbl_contr_emm_fac_df_pCorr <- cbind(Variable, Time, tbl_contr_emm_fac_df_pCorr[c(2, 7, 4:6)])

tbl_contr_emm_fac_df_eff <- cbind(Variable, Time, tbl_contr_emm_fac_df_eff)
tbl_contr_emm_fac_df_eff <- dplyr::filter(tbl_contr_emm_fac_df_eff, !grepl("BART_Eff_z", .id)) # Drop BART from Eff
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[c(1,2,4,5,9,6:8)]
```
```{r tab.cap = "Mixed Model Group Contrasts for Cognition Speed.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_AvRT
```
```{r tab.cap = "Mixed Model Group Contrasts for Cognition Accuracy.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_pCorr
```
```{r tab.cap = "Mixed Model Group Contrasts for Cognition Efficiency.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_eff
```
##Contrasts for Comparing Time Points During Bed Rest
```{r contrasts for groups by group}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3
model_emmeans <- ~ time.f
# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c("group_3")
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList) 
# Sort by Time point
tbl_contr_emm_fac_df$Contrast <- factor(tbl_contr_emm_fac_df$Contrast, levels=c("HDT3 - HDT1", "HDT5 - HDT1", "HDT14 - HDT1", "HDT28 - HDT1", "HDT42 - HDT1", "HDT57 - HDT1","(R+1) - HDT1", "(R+5) - HDT1", "(R+12) - HDT1"))
tbl_contr_emm_fac_df <- arrange(tbl_contr_emm_fac_df, .id, Contrast) 

# Add variables
# AvRT
tbl_contr_emm_fac_df_AvRT <- dplyr::filter(tbl_contr_emm_fac_df, grepl("AvR", .id))
#tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT[c(8:9, 2, 7, 4:6)]

tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT %>%
  filter(.id == "MP_AvRT_z" | .id == "AM_AvRT_z" | .id == "DSST_AvRT_z" | .id == "ERT_AvRT_z"  | .id == "MRT_AvRT_z" | .id == "PVT_AvRT_z")
  
# pCorr
tbl_contr_emm_fac_df_pCorr <- dplyr::filter(tbl_contr_emm_fac_df, grepl("pCorr", .id))
#tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr[c(8:9, 2, 7, 4:6)]

# Eff
tbl_contr_emm_fac_df_eff <- dplyr::filter(tbl_contr_emm_fac_df, grepl("Eff", .id))
#tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[c(8:9, 2, 7, 4:6)]

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) -1 
  length(levels(tbl_contr_emm_fac_df$time.f)) -1

Variable <- c("MP", rep("", tmp_n_dvs),
                                   "VOLT", rep("", tmp_n_dvs),
                                   "NBCK", rep("", tmp_n_dvs),
                                   "AM", rep("", tmp_n_dvs),
                                   "LOT", rep("", tmp_n_dvs),
                                   "ERT", rep("", tmp_n_dvs),
                                   "MRT", rep("", tmp_n_dvs),
                                   "DSST", rep("", tmp_n_dvs),
                                   "BART", rep("", tmp_n_dvs),
                                   "PVT", rep("", tmp_n_dvs))

Variable_red <- c("MP", rep("", tmp_n_dvs),
                                   "AM", rep("", tmp_n_dvs),
                                   "ERT", rep("", tmp_n_dvs),
                                   "MRT", rep("", tmp_n_dvs),
                                   "DSST", rep("", tmp_n_dvs),
                                   "PVT", rep("", tmp_n_dvs))

# Add to parameters to tables
tbl_contr_emm_fac_df_AvRT <- cbind(Variable_red, tbl_contr_emm_fac_df_AvRT[c(2, 6, 3:5)])

tbl_contr_emm_fac_df_pCorr <- cbind(Variable, tbl_contr_emm_fac_df_pCorr[c(2, 6, 3:5)])

tbl_contr_emm_fac_df_eff <- cbind(Variable, tbl_contr_emm_fac_df_eff)
tbl_contr_emm_fac_df_eff <- dplyr::filter(tbl_contr_emm_fac_df_eff, !grepl("BART_Eff_z", .id)) # Drop BART from Eff
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[c(1,3,7,4,5,6)]
```
```{r tab.cap = "Mixed Model Contrasts for Time Effect Across Groups for Cognition Speed.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_AvRT
```
```{r tab.cap = "Mixed Model Contrasts for Time Effect Across Groups for Cognition Accuracy", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_pCorr
```
```{r tab.cap = "Mixed Model Contrasts for Time Effect Across Groups for Cognition Efficiency.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_eff
```

##Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot emmeans for groups by time}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Draw plot
pd <- position_dodge(0.3)

# Accuracy
# Select
emm_fac_pCorr <- dplyr::filter(emm_fac, grepl("pCorr", .id))
emm_fac_pCorr <- droplevels(emm_fac_pCorr)

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_pCorr_z", "VOLT_pCorr_z", "NBCK_Av_pCorr_z", "AM_pCorr_z", "LOT_pCorr_z", "ERT_pCorr_z", "MRT_pCorr_z", "DSST_pCorr_z", "BART_pCorr_z", "PVT_pCorr_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Plot
p.cognition_emmeans_pCorr <- func_plot_line_facet(emm_fac_pCorr %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_pCorr_z", "VOLT_pCorr_z", "NBCK_Av_pCorr_z","AM_pCorr_z","LOT_pCorr_z","ERT_pCorr_z","MRT_pCorr_z", "DSST_pCorr_z", "BART_pCorr_z", "PVT_pCorr_z")))+ geom_hline(yintercept = 0, size = 0.3, linetype = "dotted") + theme(legend.key.size = unit(0.3, "cm"))

# Speed
# Select
emm_fac_AvRT <- dplyr::filter(emm_fac, grepl("AvR", .id))
emm_fac_AvRT <- droplevels(emm_fac_AvRT)

# New facet label names for variable
new_labels <- c("MP Speed", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_AvRT_z", "VOLT_AvRT_z", "NBCK_AvRT_z", "AM_AvRT_z", "LOT_AvRT_z", "ERT_AvRT_z", "MRT_AvRT_z", "DSST_AvRT_z", "BART_AvRT_z", "PVT_AvRT_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Plot
p.cognition_emmeans_AvRT <- func_plot_line_facet(emm_fac_AvRT %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_AvRT_z", "VOLT_AvRT_z", "NBCK_AvRT_z","AM_AvRT_z","LOT_AvRT_z","ERT_AvRT_z","MRT_AvRT_z", "DSST_AvRT_z", "BART_AvRT_z", "PVT_AvRT_z"))) + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted") + theme(legend.key.size = unit(0.3, "cm"))

# Efficiency
# Select
emm_fac_eff <- dplyr::filter(emm_fac, grepl("Eff", .id))
emm_fac_eff <- droplevels(emm_fac_eff)
# Drop BART and PVT from Eff
emm_fac_eff <- emm_fac_eff %>% filter(!grepl("BART_Eff_z", .id))

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "PVT")
names(new_labels) <- c("MP_Eff_z", "VOLT_Eff_z", "NBCK_Eff_z", "AM_Eff_z", "LOT_Eff_z", "ERT_Eff_z", "MRT_Eff_z", "DSST_Eff_z", "PVT_Eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Plot
p.cognition_emmeans_eff <- func_plot_line_facet(emm_fac_eff %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_Eff_z", "VOLT_Eff_z", "NBCK_Eff_z","AM_Eff_z","LOT_Eff_z","ERT_Eff_z","MRT_Eff_z", "DSST_Eff_z", "PVT_Eff_z"))) + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted") + theme(legend.key.size = unit(0.3, "cm"))
```
##Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group}
# Select HDBR data
# Drop Recovery
df_tmp <- subset(df_tmp, time.n < 11)
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- colnames(df_tmp)[c(37:66)]

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- lapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simply = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group"),
                 length(dvList)/3)
}

# Add variables
tbl_mm_fac_aov_df_AvRT <- dplyr::filter(tbl_mm_fac_aov_df, grepl("AvR", X1))

tbl_mm_fac_aov_df_pCorr <- dplyr::filter(tbl_mm_fac_aov_df, grepl("pCorr", X1))

tbl_mm_fac_aov_df_eff <- dplyr::filter(tbl_mm_fac_aov_df, grepl("Eff", X1))


# Create parameters
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / ( length(dvList)/3 ) - 1)
Variable <- c("MP", blanks,"VOLT", blanks, "NBCK", blanks, "AM", blanks, "LOT", blanks, "ERT", blanks, "MRT", blanks, "DSST", blanks, "BART", blanks, "PVT", blanks)

# Add to parameters to tables
tbl_mm_fac_aov_df_AvRT <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_AvRT[c(4:7)])
tbl_mm_fac_aov_df_pCorr <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_pCorr[c(4:7)])

tbl_mm_fac_aov_df_eff <- cbind(Variable, Parameter, tbl_mm_fac_aov_df_eff)
tbl_mm_fac_aov_df_eff <- dplyr::filter(tbl_mm_fac_aov_df_eff, !grepl("BART_Eff_z", X1)) # Drop BART from Eff
tbl_mm_fac_aov_df_eff <- tbl_mm_fac_aov_df_eff[-c(3:5)]
```
```{r tab.cap = "Mixed Model Summary testing the Main Effect of Group for Cognition: Speed.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_AvRT <- tbl_mm_fac_aov_df_AvRT %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_AvRT
```
```{r tab.cap = "Mixed Model Summary testing the Main Effect of Group for Cognition: Accuracy", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_pCorr <- tbl_mm_fac_aov_df_pCorr %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_pCorr
```
```{r tab.cap = "Mixed Model Summary testing the Main Effect of Group for Cognition: Efficiency.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_eff <- tbl_mm_fac_aov_df_eff %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_eff
```
##Contrasts for Comparing Groups
```{r contrasts for groups}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Add variables
# AvRT
tbl_contr_emm_fac_df_AvRT <- dplyr::filter(tbl_contr_emm_fac_df, grepl("AvR", .id))
#tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT[c(8:9, 2, 7, 4:6)]

# pCorr
tbl_contr_emm_fac_df_pCorr <- dplyr::filter(tbl_contr_emm_fac_df, grepl("pCorr", .id))
#tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr[c(8:9, 2, 7, 4:6)]

# Eff
tbl_contr_emm_fac_df_eff <- dplyr::filter(tbl_contr_emm_fac_df, grepl("Eff", .id))
#tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[c(8:9, 2, 7, 4:6)]


# Create vars to make nice table
Variable <- c("MP", rep("", 2),
                                   "VOLT", rep("", 2),
                                   "NBCK", rep("", 2),
                                   "AM", rep("", 2),
                                   "LOT", rep("", 2),
                                   "ERT", rep("", 2),
                                   "MRT", rep("", 2),
                                   "DSST", rep("", 2),
                                   "BART", rep("", 2),
                                   "PVT", rep("", 2))

# Add to parameters to tables
tbl_contr_emm_fac_df_AvRT <- cbind(Variable, tbl_contr_emm_fac_df_AvRT[c(2, 6, 3:5)])

tbl_contr_emm_fac_df_pCorr <- cbind(Variable, tbl_contr_emm_fac_df_pCorr[c(2, 6, 3:5)])

tbl_contr_emm_fac_df_eff <- cbind(Variable, tbl_contr_emm_fac_df_eff[c(2, 6, 3:5)])

# Drop BART from Eff
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff[-c( 25:27),]
```
```{r tab.cap = "Mixed Model Contrasts Comparing Groups for Cognition: Speed.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_AvRT <- tbl_contr_emm_fac_df_AvRT %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_AvRT
```
```{r tab.cap = "Mixed Model Contrasts Comparing Groups for Cognition: Accuracy.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_pCorr <- tbl_contr_emm_fac_df_pCorr %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_pCorr
```
```{r tab.cap = "Mixed Model Contrasts Comparing Groups for Cognition: Efficiency.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_eff <- tbl_contr_emm_fac_df_eff %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_eff
```
##Plot Estimated Marignal Means for Comparing Groups
```{r plot groups}
# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Positioning
pd <- position_dodge(0.99)

# AvRT
emm_fac_AvRT <- dplyr::filter(emm_fac, grepl("AvR", .id))
emm_fac_AvRT <- droplevels(emm_fac_AvRT)

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_AvRT_z", "VOLT_AvRT_z", "NBCK_AvRT_z", "AM_AvRT_z", "LOT_AvRT_z", "ERT_AvRT_z", "MRT_AvRT_z", "DSST_AvRT_z", "BART_AvRT_z", "PVT_AvRT_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw Plot 
p.cognition_emmeans_AvRT_main <- func_plot_bar_facet(emm_fac_AvRT %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_AvRT_z", "VOLT_AvRT_z", "NBCK_AvRT_z","AM_AvRT_z","LOT_AvRT_z","ERT_AvRT_z","MRT_AvRT_z", "DSST_AvRT_z", "BART_AvRT_z", "PVT_AvRT_z"))) + theme(legend.key.size = unit(0.3, "cm"))


# Accuracy
# Select
emm_fac_pCorr <- dplyr::filter(emm_fac, grepl("pCorr", .id))
emm_fac_pCorr <- droplevels(emm_fac_pCorr)

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "BART", "PVT")
names(new_labels) <- c("MP_pCorr_z", "VOLT_pCorr_z", "NBCK_Av_pCorr_z", "AM_pCorr_z", "LOT_pCorr_z", "ERT_pCorr_z", "MRT_pCorr_z", "DSST_pCorr_z", "BART_pCorr_z", "PVT_pCorr_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw Plot 
p.cognition_emmeans_pCorr_main <- func_plot_bar_facet(emm_fac_pCorr %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_pCorr_z", "VOLT_pCorr_z", "NBCK_Av_pCorr_z","AM_pCorr_z","LOT_pCorr_z","ERT_pCorr_z","MRT_pCorr_z", "DSST_pCorr_z", "BART_pCorr_z", "PVT_pCorr_z"))) + theme(legend.key.size = unit(0.3, "cm"))


# Efficiency
# Select
emm_fac_eff <- dplyr::filter(emm_fac, grepl("Eff", .id))
emm_fac_eff <- droplevels(emm_fac_eff)
# Drop BART from Eff
emm_fac_eff <- emm_fac_eff[-c( 25:27),]

# New facet label names for variable
new_labels <- c("MP", "VOLT", "NBACK", "AM", "LOT", 
                      "ERT", "MRT", "DSST", "PVT")
names(new_labels) <- c("MP_Eff_z", "VOLT_Eff_z", "NBCK_Eff_z", "AM_Eff_z", "LOT_Eff_z", "ERT_Eff_z", "MRT_Eff_z", "DSST_Eff_z", "PVT_Eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

# Define grid
facet_grid_def <- facet_wrap(~ .id,
                             switch = "y",
                             ncol = 1,
                             labeller = labeller_def) 

# Draw Plot 
p.cognition_emmeans_eff_main <- func_plot_bar_facet(emm_fac_eff %>%
                                                  mutate(group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"),
                                                         .id = fct_relevel(.id, "MP_Eff_z", "VOLT_Eff_z", "NBCK_Eff_z","AM_Eff_z","LOT_Eff_z","ERT_Eff_z","MRT_Eff_z", "DSST_Eff_z", "PVT_Eff_z"))) + theme(legend.key.size = unit(0.3, "cm"))
```
##Create Combined plot Speed
```{r plot combined speed}
# Combine plot 
p.cognition_comb_speed <- plot_grid(p.cognition_desc_AvRT,
                                  p.cognition_emmeans_AvRT_main + rremove("x.text") + theme( strip.text.y = element_blank() ),
                                  labels = c("a", "b"), label_size = 10,
                                  ncol = 2, nrow = 1, rel_widths = c(2.4, 0.6)
                                  )
# Adjust legend size
p.cognition_comb_speed <- p.cognition_comb_speed + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Cognition/p.cognition_comb_speed.pdf",
    width = 32/2.54, 
    height = 22/2.54,
    useDingbats=FALSE) #in cm
print(p.cognition_comb_speed)
dev.off()
```

```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 8, fig.height = 9, echo = FALSE, fig.cap = "Cognition. (a) Time course of speed before, during, and after bed rest. Means within groups are shifted to reflect a pre-HDT baseline performance of 0 (zero). (b) Main effect of bed rest. Data means and SE are adjusted for baseline, age, and sex."}
p.cognition_comb_speed
```

##Create Combined plot Accuracy
```{r plot combined acc}
# Combine plot 
p.cognition_comb_acc <- plot_grid(p.cognition_desc_pCorr,
                                  p.cognition_emmeans_pCorr_main + rremove("x.text") + theme( strip.text.y = element_blank() ),
                                  labels = c("a", "b"),label_size = 10,
                                  ncol = 2, nrow = 1, rel_widths = c(2.4, 0.6)
                                  )

# Adjust legend size
p.cognition_comb_acc <- p.cognition_comb_acc + theme( legend.key.size = unit(0.3, "cm") )

# Save plot as pdf
pdf("./Figures/Cognition/p.cognition_comb_acc.pdf",
    width = 22/2.54, 
    height = 32/2.54,
    useDingbats=FALSE) #in cm
print(p.cognition_comb_acc)
dev.off()
```
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 8, fig.height = 9, echo = FALSE, fig.cap = "Cognition. (a) Time course of accuracy before, during, and after bed rest. Means within groups are shifted to reflect a pre-HDT baseline performance of 0 (zero). (b) Main effect of bed rest. Data means and SE are adjusted for baseline, age, and sex."}
p.cognition_comb_acc
```
##Create Combined plot Efficiency
```{r plot combined eff}
# Combine plot 
p.cognition_eff_comb <- plot_grid(p.cognition_desc_eff, p.cognition_emmeans_eff_main + rremove("x.text") + theme( strip.text.y = element_blank() ),
                                  labels = c("a", "b"), label_size = 10,
                                  ncol = 2, nrow = 1, rel_widths = c(2.4, 0.6)
                                  )

# Adjust legend size
p.cognition_eff_comb <- p.cognition_eff_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Cognition/p.cognition_eff_comb.pdf",
    width = 22/2.54, 
    height = 30/2.54,
    useDingbats=FALSE) #in cm
print(p.cognition_eff_comb)
dev.off()
```
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 8, fig.height = 9, echo = FALSE, fig.cap = "Cognition. (a) Time course of efficiency before, during, and after bed rest. Means within groups are shifted to reflect a pre-HDT baseline performance of 0 (zero). (b) Main effect of bed rest. Data means and SE are adjusted for baseline, age, and sex."}
p.cognition_eff_comb
```