---
title: "AGBRESA Executive Control"
author: "A Stahn"
date: "11/08/2021"
output: html_document
---
```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
# Prepare Script
## Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(nlme)
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using cowplot
```
## Print Session Info
```{r print R and package versions}
print(sessionInfo())
```
## Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report_white  <-  theme_pubr() + theme(
  axis.line = element_line(size = 0.5 / ggplot_factor_line,color="black"),
  axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
  axis.ticks.length = unit(0.2, "cm"), 
  text = element_text(size = 8 * ggplot_factor_font,
                      family="Helvetica",
                      colour="black"),
  axis.text.x=element_text(angle = 0, 
                           vjust = 0.5,
                           size = 8 * ggplot_factor_font,
                           family = "Helvetica",
                           colour = "black"), #face="bold"
  axis.text.y = element_text(angle = 0,
                            vjust=0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour="black"),
  axis.title.x = element_text(angle = 0,
                            vjust =0.5,
                            size= 8 * ggplot_factor_font,
                            family="Helvetica",
                            colour="black",
                            face="bold"),
  axis.title.y = element_text(angle = 90,
                            vjust = 0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour = "black",
                            face = "bold") # face = "bold" 
  )
```
## Load Data
```{r load data}
#  Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], as.factor)

# Dual Task
df_dual <- read_excel("./Data/Data Executive Control.xlsx",
                          sheet = "Data Dual z")
df_dual[c(1:5)] <- lapply(df_dual[c(1:5)], as.factor)

# Switch Task
df_switch <- read_excel("./Data/Data Executive Control.xlsx",
                        sheet = "Data Switch z")
df_switch[c(1:6)] <- lapply(df_switch[c(1:6)], as.factor)
```

# Definition of Helper Functions 
## Descriptive Functions
```{r functions for descriptive stats}
# Function to check data completion 
func_data_completion <- function(data, ...) {
  
  if(!"time.f" %in% names(data)) {
    data$time.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  if(!"cond.f" %in% names(data)) {
    data$cond.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )  %>%
  
  group_by(variable) %>%
  dplyr::summarise(
      N = 24 * length( levels(time.f) ) * length( levels(cond.f) ),
      n = sum( !is.na(value) ),
      Percent = n / N * 100
      )
}

# Function to compute descriptives
func_desc <- function(data, ...) {
  df_tmp <- df_demo[ , !names(df_demo) %in% c("age","height", "weight")]
  data <- merge(df_tmp, data, by = "id") #add demo
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )
  groups <- enquos(...)
  
  result <- data %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      MEAN = mean(value, na.rm = T),
      SE = sd(value, na.rm = T) / sqrt(length(value) )
      )
  return(result)
}
```
## Plot Functions
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report_white +
    geom_line(position = pd) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4, 
                  position = pd) +
    geom_point(position = pd,
               shape = 21,
               size = 2) + #shape = 21, size = 1, fill = "white"
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10) +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 10))
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}

# Function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report_white +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none") +
    theme(legend.title = element_blank(),
          legend.text = element_text(size=8),
          axis.title.x = element_text(size = 10),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}

# Function for bar plots, takes 'desc*' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}
```
## Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for appending bdc data as covariate
func_bdc_cov <- function(data, ...) {
  
  df_tmp <- subset(data, time.f != bdc)
  
  df_tmp_pre <- subset(data, time.f == bdc) %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .)) %>%
    select("id" | is.numeric)
  
  df_tmp <- merge(df_tmp_pre, df_tmp, by = "id")
  droplevels(df_tmp)
  
  df_tmp <- merge(df_demo, df_tmp,by  = c("id")) 
}

# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML = T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

# Function for creating mixed model tables, takes 'dvList'
func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f); also requires 'func_mm_fac_with_bdc_adj_help'
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Helper function contrasts emmeans, takes 'dvList'; also requires 'func_mm_fac_with_bdc_adj_help'
func_contrasts_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac_with_bdc_adj <- function(dvList) {
  tmp <- func_contrasts_emm_fac_with_bdc_adj(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```

# Data Completion Check
```{r descriptive summaries for completed (missing) data}
# Dual Task
missing_dual <-  func_data_completion(df_dual)
missing_dual$n <- missing_dual$n/13
missing_dual$Percent <- missing_dual$Percent/13 #correct for additional conditions: time.f task stimType target

# Switch Task
bdc <- "BDC-6"
missing_switch <-  func_data_completion(df_switch)
missing_switch$n <- missing_switch$n/12 # correct for conditions: 2 time.f * 2 task * 2 cti * 2 type * 2 valence
missing_switch$Percent <- missing_switch$Percent/12 # correct for conditions: 2 time.f * 2 task * 2 cti * 2 type * 2 valence

# Combine summary
exec_bat_summary <- bind_rows(missing_dual[1,], 
                              missing_switch[1,]) 

exec_bat_summary$Task <- c("Dual Task", 
                           "Switch Task")

exec_bat_summary <- exec_bat_summary[c(5,2:4)]
colnames(exec_bat_summary)[2] <- "Expected (N)"
colnames(exec_bat_summary)[3] <- "Completed (N)"
colnames(exec_bat_summary)[4] <- "Completed (%)"
exec_bat_summary <- as.data.frame(exec_bat_summary)
```
#### Table 1. Data collection summary Executive Control.
```{r echo = FALSE}
datatable(exec_bat_summary) %>%
    formatRound(columns=c("Completed (%)"), digits = 1)

round(mean(exec_bat_summary$'Completed (%)'), 1)
```

# Dual Task
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline dual}
# Plot arithmetic means
desc <- func_desc(df_dual, variable, time.f, group_3, task)

# Drop vars
desc <- subset(desc, variable != "miss_z" & variable != "incorrect_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","accuracy_z", "eff_acc_z")

new_labels2 <- c("Dual", "Auditory", "Visual") 
names(new_labels2) <- c("dual", "singleAud", "singleVis")


# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   task = new_labels2)

facet_grid_def <- facet_grid(variable ~ task,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.dual_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z","accuracy_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.dual_desc <- p.dual_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.dual_desc <- p.dual_desc + theme(legend.key.size = unit(0.3, "cm"))

```
#### Mixed Model Comparing Groups
```{r echo = FALSE}
# Add baseline as cov
bdc <- "BDC-6"
df_tmp <-  func_bdc_cov(df_dual)

df_tmp <-  df_dual

# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-6")
colnames(df_tmp_pre)[c(6:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(6:ncol(df_tmp_pre))], 
                                                     sep = "_")

df_tmp <- subset(df_tmp, time.f != "BDC-6") # Drop baseline
df_tmp <- droplevels(df_tmp)

df_tmp <- merge(df_tmp[-c(2)], df_tmp_pre[-c(2)], by = c("id", "task", "stimType", "target") )
df_tmp <- merge(df_demo, df_tmp, by = c("id")) # Add demo

# Select dep vars
dvList <- c("rt_z","accuracy_z", "eff_acc_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * task", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_dual <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 2. Mixed Model Summary for Dual Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_dual, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between groups dual}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3 * task

# Define contrasts
contrast_type <- "pairwise"
factors <- c("task")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$task)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Dual", rep("", tmp_n_cond),
                                          "Auditory",rep("", tmp_n_cond),
                                          "Visual",rep("", tmp_n_cond)),
                                        length(dvList) )

# Table for contrasts
tbl_contr_emm_fac_df_dual <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 4:6)]
```
#### Table 3. Mixed Model Group Contrasts for Dual Task.
```{r echo = FALSE}
# print table
datatable(tbl_contr_emm_fac_df_dual, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups dual}
# Define model for emmeans
model_emmeans <- ~ group_3 * task

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed (z)","Accuracy (z)","Efficiency (z)")
names(new_labels) <- c("rt_z", "accuracy_z","eff_acc_z")

new_labels2 <- c("Dual", "Auditory", "Visual") 
names(new_labels2) <- c("dual", "singleAud", "singleVis")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   task = new_labels2)

facet_grid_def <- facet_grid(.id ~ task,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.dual_emmeans <- func_plot_bar_facet(emm_fac %>%
                                        mutate(.id = fct_relevel(.id, "rt_z","accuracy_z", "eff_acc_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.dual_emmeans <- p.dual_emmeans + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Executive Control/p.dual_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats=FALSE) #in cm
print(p.dual_emmeans)
dev.off()
```
#### Figure 1. Dual Task: Effects of Bed Rest on Speed, Accuracy, and Efficiency on R+1. Data are means and SE adjusted for baseline.
```{r, echo = FALSE, fig.width = 5, fig.height = 8, fig.cap = ""}
print(p.dual_emmeans)
```

# Switch Task
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline switch}
# Plot arithmetic means
desc <- func_desc(df_switch, variable, time.f, group_3, task, type)

# Drop vars
desc <- subset(desc, variable != "miss_z" & variable != "incorrect_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed (z)","Accuracy (z)","Efficiency (z)")
names(new_labels) <- c("rt_z","accuracy_z","eff_acc_z")

new_labels2 <- c("MB", "PRB") 
names(new_labels2) <- c("mb", "prb")

new_labels3 <- c("Rep", "Switch") 
names(new_labels3) <- c("rep", "switch")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                         task = new_labels2,
                         type = new_labels3)

facet_grid_def <- facet_grid(variable + task ~ type,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 


# Draw plot
pd <- position_dodge(0.3)
p.switch_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z","accuracy_z", "eff_acc_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.switch_desc <- p.switch_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.switch_desc <- p.switch_desc + theme( legend.key.size = unit(0.3, "cm") )
```
#### Mixed Model Comparing Groups
```{r echo = FALSE}
df_tmp <- df_switch

# Subset to switch blocks
df_tmp <- subset(df_tmp, task == "mb")

# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-6")
colnames(df_tmp_pre)[c(7:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(7:ncol(df_tmp_pre))], 
                                                     sep = "_")

df_tmp <- subset(df_tmp, time.f != "BDC-6") # Drop baseline
df_tmp <- droplevels(df_tmp)

df_tmp <- merge(df_tmp[-c(2)], df_tmp_pre[-c(2)], by = c("id", "task", "cti", "type", "valence") )
df_tmp <- merge(df_demo, df_tmp, by = c("id")) # Add demo

# Select dep vars
dvList <- c("rt_z","accuracy_z","eff_acc_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * type", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks, "Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_switch <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 4. Mixed Model Summary for Switch Task.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_switch, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between groups switch}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3 * type

# Define contrasts
contrast_type <- "pairwise"
factors <- c("type")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$type)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Repeated", rep("", tmp_n_cond),
                                          "Switch",rep("", tmp_n_cond)),
                                        length(dvList) )

# Table for contrasts
tbl_contr_emm_fac_df_switch <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 4:6)]
```
#### Table 5. Mixed Model Group Contrasts for Switch Task.
```{r echo = FALSE}
# print table
datatable(tbl_contr_emm_fac_df_switch, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups switch}
# Define model for emmeans
model_emmeans <- ~ group_3 * type

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed (z)", "Accuracy (z)", "Efficiency (z)")
names(new_labels) <- c("rt_z", "accuracy_z", "eff_acc_z")

new_labels2 <- c("Repeated", "Switch") 
names(new_labels2) <- c("rep", "switch")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                         type = new_labels2)

facet_grid_def <- facet_grid(.id ~ type,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.switch_emmeans <- func_plot_bar_facet(emm_fac %>%
                                          mutate(.id = fct_relevel(.id, "rt_z", "heading_error_z", "distance_z"),
                                                 group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))


# Adjust legend size
p.switch_emmeans <- p.switch_emmeans + theme( legend.key.size = unit(0.3, "cm") )

# Save plot as pdf
pdf("./Figures/Executive Control/p.switch_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.switch_emmeans)
dev.off()
```

#### Figure 2. Switch Task: Effect of bed rest on speed, accuracy, and efficiency on R+1. Data are means and SE adjusted for baseline.
```{r, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap = ""}
print(p.switch_emmeans)
```
