---
title: "Appendix Final Report HyperCampus Spatial Cognition 2"
#author: "A Stahn"
#date: "10/27/2021"
#output:
 # officedown::rdocx_document
  #word_document:
    #number_sections: TRUE
    #fig_caption: TRUE
  #bookdown::html_document2:
  #number_sections: TRUE
  #fig_caption: TRUE
  #always_allow_html: true
output:  
  officedown::rdocx_document:
    tables:
      table.align: "center"
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
        text.align: "left"
    plots:
      align: left
      caption:
        sep: '. '
---
```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, dpi = 300, echo = FALSE)
```
##Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(nlme)
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using cowplot
library(officedown)
library(officer)
library(flextable)
```
##Print Session Info
```{r print R and package versions}
print(sessionInfo())
```

##Load Data
```{r load data}
#  Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], as.factor)

# Dual Task
df_dual <- read_excel("./Data/Data Executive Control.xlsx",
                          sheet = "Data Dual z")
df_dual[c(1:5)] <- lapply(df_dual[c(1:5)], as.factor)

# Switch Task
df_switch <- read_excel("./Data/Data Executive Control.xlsx",
                        sheet = "Data Switch z")
df_switch[c(1:6)] <- lapply(df_switch[c(1:6)], as.factor)
```
##Descriptive Functions
#Functions Descritpive Stats
```{r functions for descriptive stats}
# Function to check data completion 
func_data_completion <- function(data, ...) {
  
  if(!"time.f" %in% names(data)) {
    data$time.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  if(!"cond.f" %in% names(data)) {
    data$cond.f <- as.factor( c( rep(1, nrow(data) ) ) )
    }
  
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )  %>%
  
  group_by(variable) %>%
  dplyr::summarise(
      N = 24 * length( levels(time.f) ) * length( levels(cond.f) ),
      n = sum( !is.na(value) ),
      Percent = n / N * 100
      )
}

# Function to compute descriptives
func_desc <- function(data, ...) {
  df_tmp <- df_demo[ , !names(df_demo) %in% c("age","height", "weight")]
  data <- merge(df_tmp, data, by = "id") #add demo
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )
  groups <- enquos(...)
  
  result <- data %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      MEAN = mean(value, na.rm = T),
      SE = sd(value, na.rm = T) / sqrt(length(value) )
      )
  return(result)
}

func_bdc_correction <- function(data,..){
 df_tmp <- data %>%
    subset(time.f == bdc) %>%
    group_by(group_3, variable) %>%
    dplyr::summarise(
      mean_bdc_by_group = mean(MEAN, na.rm = T)
      )
  
  df_tmp <- merge(df_tmp, data, by = c("group_3", "variable") )
  df_tmp <- df_tmp %>%
    mutate(MEAN_corr = case_when(time.f == bdc ~
                              MEAN-mean_bdc_by_group,
                            TRUE ~ MEAN)) %>%
    select( c(!mean_bdc_by_group & !MEAN) ) %>%
    dplyr::rename(MEAN = MEAN_corr)
  }
```
##Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for appending bdc data as covariate
func_bdc_cov <- function(data, ...) {
  
  df_tmp <- subset(data, time.f != bdc)
  
  df_tmp_pre <- subset(data, time.f == bdc) %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .)) %>%
    select("id" | is.numeric)
  
  df_tmp <- merge(df_tmp_pre, df_tmp, by = "id")
  droplevels(df_tmp)
  
  df_tmp <- merge(df_demo, df_tmp,by  = c("id")) 
}

# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML = T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

# Function for creating mixed model tables, takes 'dvList'
func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f); also requires 'func_mm_fac_with_bdc_adj_help'
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Helper function contrasts emmeans, takes 'dvList'; also requires 'func_mm_fac_with_bdc_adj_help'
func_contrasts_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "fdr"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac_with_bdc_adj <- function(dvList) {
  tmp <- func_contrasts_emm_fac_with_bdc_adj(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```
#Functions tables
```{r functions for flextable}
theme_tableflex_report <- function(x, ...) {
  std_b <- fp_border(width = 1.5, color = "black")
  thin_b <- fp_border(width = 0.5, color = "black")
    x <- border_remove(x)
    x <- hline(x, border = thin_b, part = "all")
    x <- hline_top(x, border = std_b, part = "header")
    x <- hline_bottom(x, border = std_b, part = "header")
    x <- hline_bottom(x, border = std_b, part = "body")
    x <- bold(x = x, bold = TRUE, part = "header")
    x <- align_text_col(x, align = "left", header = TRUE)
    x <- align_nottext_col(x, align = "center", header = TRUE)
    fix_border_issues(x)
    autofit(x)
}

set_flextable_defaults(
  font.size = 10,
  font.family = "Times New Roman",
  theme_fun = theme_tableflex_report)
  #padding = 6)
  #background.color = "#EFEFEF")
```
#Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report <- function(base_size = 8) {
  theme_pubr() + #%+replace%
    theme(
      plot.margin = margin(0, 0, 0, 0, "cm"),
      text = element_text(size = 8,
                      colour="black"), #family="Helvetica"
      # axes
      axis.title = element_text(size = 8, face = "bold"), #vjust = 0.5
      axis.text = element_text(size = 8), #angle = 0
      axis.line = element_line(size = 0.5 / ggplot_factor_line, color="black"),
      axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
      axis.ticks.length = unit(0.2, "cm"), 
      # legend
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.title = element_blank(),
      legend.text = element_text(size = 8),
      axis.title.x = element_text(size = 8),
      # facetting
      strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5),
                                          #linetype = "solid"),
          strip.text = element_text(size = 8,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(1.5, "lines")
    )
}

```
#Functions Plotting
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report() +
    geom_line(position = pd,
              size = 0.3) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4,
                  size = 0.3,
                  position = pd) +
    geom_point(position = pd,
               #shape = 21,
               size = 2) +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10)
    #scale_shape_manual(values=c(3, 16, 17))+
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def
}


# Function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report() +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none")
}

# Function for bar plots, takes 'desc*' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def
}
```
# Data Completion Check
```{r descriptive summaries for completed (missing) data}
# Dual Task
missing_dual <-  func_data_completion(df_dual)
missing_dual$n <- missing_dual$n/13
missing_dual$Percent <- missing_dual$Percent/13 #correct for additional conditions: time.f task stimType target

# Switch Task
bdc <- "BDC-6"
missing_switch <-  func_data_completion(df_switch)
missing_switch$n <- missing_switch$n/12 # correct for conditions: 2 time.f * 2 task * 2 cti * 2 type * 2 valence
missing_switch$Percent <- missing_switch$Percent/12 # correct for conditions: 2 time.f * 2 task * 2 cti * 2 type * 2 valence

# Combine summary
exec_bat_summary <- bind_rows(missing_dual[1,], 
                              missing_switch[1,]) 

exec_bat_summary$Task <- c("Dual Task", 
                           "Switch Task")

exec_bat_summary <- exec_bat_summary[c(5,2:4)]
colnames(exec_bat_summary)[2] <- "Expected (N)"
colnames(exec_bat_summary)[3] <- "Completed (N)"
colnames(exec_bat_summary)[4] <- "Completed (%)"
exec_bat_summary <- as.data.frame(exec_bat_summary)
```
```{r tab.cap = "Data collection summary Executive Control.", tab.cap.style = "Table Caption", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
exec_bat_summary <- exec_bat_summary %>% flextable() %>% autofit() %>% 
  colformat_double(j = c("Completed (%)"), digits = 1) 
# Print
exec_bat_summary
```
# Dual Task
##Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline dual}
# Plot arithmetic means
desc <- func_desc(df_dual, variable, time.f, group_3, task)

# Drop vars
desc <- subset(desc, variable != "miss_z" & variable != "incorrect_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","accuracy_z", "eff_acc_z")

new_labels2 <- c("Dual", "Auditory", "Visual") 
names(new_labels2) <- c("dual", "singleAud", "singleVis")


# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                                   task = new_labels2)

facet_grid_def <- facet_grid(variable ~ task,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.dual_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z","accuracy_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.dual_desc <- p.dual_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.dual_desc <- p.dual_desc + theme(legend.key.size = unit(0.3, "cm"))
```
##Mixed Model Comparing Groups
```{r echo = FALSE}
# Add baseline as cov
bdc <- "BDC-6"
df_tmp <-  func_bdc_cov(df_dual)

df_tmp <-  df_dual

# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-6")
colnames(df_tmp_pre)[c(6:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(6:ncol(df_tmp_pre))], 
                                                     sep = "_")

df_tmp <- subset(df_tmp, time.f != "BDC-6") # Drop baseline
df_tmp <- droplevels(df_tmp)

df_tmp <- merge(df_tmp[-c(2)], df_tmp_pre[-c(2)], by = c("id", "task", "stimType", "target") )
df_tmp <- merge(df_demo, df_tmp, by = c("id")) # Add demo

# Select dep vars
dvList <- c("rt_z","accuracy_z", "eff_acc_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * task", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "Group x Task Condition"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_dual <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
```{r tab.cap = "Mixed Model Summary for Dual Task.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_dual <- tbl_mm_fac_aov_df_dual %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_dual
```
##Contrasts for Group Comparisons
```{r contrasts between groups dual}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3 * task

# Define contrasts
contrast_type <- "pairwise"
factors <- c("task")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$task)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Condition <- rep ( c("Dual", rep("", tmp_n_cond),
                                          "Auditory",rep("", tmp_n_cond),
                                          "Visual",rep("", tmp_n_cond)),
                                        length(dvList) )

# Table for contrasts
tbl_contr_emm_fac_df_dual <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 4:6)]
```
```{r tab.cap = "Mixed Model Group Contrasts for Dual Task.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_dual <- tbl_contr_emm_fac_df_dual %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_dual
```
##Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups dual}
# Define model for emmeans
model_emmeans <- ~ group_3 * task

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "accuracy_z","eff_acc_z")

new_labels2 <- c("Dual", "Auditory", "Visual") 
names(new_labels2) <- c("dual", "singleAud", "singleVis")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                                   task = new_labels2)

facet_grid_def <- facet_grid(.id ~ task,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.dual_emmeans <- func_plot_bar_facet(emm_fac %>%
                                        mutate(.id = fct_relevel(.id, "rt_z","accuracy_z", "eff_acc_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.dual_emmeans <- p.dual_emmeans + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Executive Control/p.dual_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats=FALSE) #in cm
print(p.dual_emmeans)
dev.off()

# Dual only
facet_grid_def <- facet_grid(task ~ .id ,
                             switch = "y",
                             labeller = labeller_def) 

p.dual_emmeans_dual <- func_plot_bar_facet(subset(emm_fac, task == "dual") %>%
                                        mutate(.id = fct_relevel(.id, "rt_z","accuracy_z", "eff_acc_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.dual_emmeans_dual <- p.dual_emmeans_dual + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Executive Control/p.dual_emmeans_dual.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats=FALSE) #in cm
print(p.dual_emmeans_dual)
dev.off()

```
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 3, fig.height = 8, echo = FALSE, fig.cap = "Dual Task: Effects of Bed Rest on Speed, Accuracy, and Efficiency on R+1. Data are means and SE adjusted for baseline, age, and sex."}
p.dual_emmeans
```
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 3, fig.height = 2.5, echo = FALSE, fig.cap = "Dual Task: Effects of Bed Rest on Speed, Accuracy, and Efficiency on R+1. Data are means and SE adjusted for baseline, age, and sex."}
p.dual_emmeans_dual
```
# Switch Task
##Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline switch}
# Plot arithmetic means
desc <- func_desc(df_switch, variable, time.f, group_3, task, type)

# Drop vars
desc <- subset(desc, variable != "miss_z" & variable != "incorrect_z")

# Plot desc 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","accuracy_z","eff_acc_z")

new_labels2 <- c("MB", "PRB") 
names(new_labels2) <- c("mb", "prb")

new_labels3 <- c("Rep", "Switch") 
names(new_labels3) <- c("rep", "switch")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels,
                         task = new_labels2,
                         type = new_labels3)

facet_grid_def <- facet_grid(variable + task ~ type,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 


# Draw plot
pd <- position_dodge(0.3)
p.switch_desc <- func_plot_line_facet(desc %>%
                                     mutate(variable = fct_relevel(variable, "rt_z","accuracy_z", "eff_acc_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.switch_desc <- p.switch_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.switch_desc <- p.switch_desc + theme( legend.key.size = unit(0.3, "cm") )
```
##Mixed Model Comparing Groups
```{r echo = FALSE}
df_tmp <- df_switch

# Subset to switch blocks
df_tmp <- subset(df_tmp, task == "mb")

# Add baseline as cov
df_tmp_pre <- subset(df_tmp, time.f =="BDC-6")
colnames(df_tmp_pre)[c(7:ncol(df_tmp_pre))] <- paste("pre", colnames(df_tmp_pre)[c(7:ncol(df_tmp_pre))], 
                                                     sep = "_")

df_tmp <- subset(df_tmp, time.f != "BDC-6") # Drop baseline
df_tmp <- droplevels(df_tmp)

df_tmp <- merge(df_tmp[-c(2)], df_tmp_pre[-c(2)], by = c("id", "task", "cti", "type", "valence") )
df_tmp <- merge(df_demo, df_tmp, by = c("id")) # Add demo

# Select dep vars
dvList <- c("rt_z","accuracy_z","eff_acc_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " * type", " * cti", " * valence", " + (1|id)" )
#model_mm <- paste0(" + sex"," + age", " + group_3", " * task", " * cti", " * valence", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group",
  "Task Condition",
  "CTI",
  "Valence",
  "Group x Task Condition",
  "Group x CTI",
  "Task Condition x CTI",
  "Group x Valence",
  "Task Condition x Valence",
  "CTI x Valence",
  "Group x Task Condition x CTI",
  "Group x Task Condition x Valence",
  "Group x CTI x Valence",
  "Task Condition x CTI x Valence",
  "Group x Task Condition x CTI x Valence"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks, "Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_switch <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
```{r tab.cap = "Mixed Model Summary for Switch Task.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_mm_fac_aov_df_switch <- tbl_mm_fac_aov_df_switch %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df2", "F"), digits = 1) %>% 
  colformat_double( j = c("P"), digits = 3 ) 
# Print
tbl_mm_fac_aov_df_switch
```
##Contrasts for Group Comparisons
```{r contrasts between groups switch}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3 * type * valence * cti

# Define contrasts
contrast_type <- "pairwise"
factors <- c("type", "cti", "valence")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$type)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1

tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 23),
                                   "Accuracy", rep("", 23),
                                   "Efficiency", rep("", 23))

tbl_contr_emm_fac_df$CTI <- rep ( c("Long", rep("", 5),
                                          "Short",rep("", 5)),
                                        length(dvList) )

tbl_contr_emm_fac_df$Condition <- rep ( c("Repeated", rep("", 2),
                                          "Switch",rep("", 2)),
                                        length(dvList) )


tbl_contr_emm_fac_df$Valence <- rep ( c("bivalent", rep("", 5),
                                          "univalent",rep("", 5)),
                                        length(dvList) )
# Table for contrasts
tbl_contr_emm_fac_df_switch <- tbl_contr_emm_fac_df[c(10:11, 2, 7, 4:6)]
```
```{r tab.cap = "Mixed Model Group Contrasts for Switch Task.", tab.topcaption = TRUE, echo = FALSE}
# Convert to word flextable
tbl_contr_emm_fac_df_switch <- tbl_contr_emm_fac_df_switch %>% flextable() %>% autofit() %>% 
  colformat_double( j = c("df", "t"), digits = 1) %>% 
  colformat_double( j = c("P (unadjusted)"), digits = 3 ) 
# Print
tbl_contr_emm_fac_df_switch
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups switch}
# Define model for emmeans
model_emmeans <- ~ group_3 * type * valence * cti

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed", "Accuracy", "Efficiency")
names(new_labels) <- c("rt_z", "accuracy_z", "eff_acc_z")

new_labels2 <- c("Repeated", "Switch") 
names(new_labels2) <- c("rep", "switch")

new_labels3 <- c("Short", "Long") 
names(new_labels3) <- c("short", "long")

new_labels4 <- c("Univalent", "Bivalent") 
names(new_labels4) <- c("univalent", "bivalent")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels,
                         type = new_labels2,
                         cti = new_labels3,
                         cti = new_labels4)

facet_grid_def <- facet_grid(.id ~ type + valence + cti,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.switch_emmeans <- func_plot_bar_facet(emm_fac %>%
                                          mutate(.id = fct_relevel(.id, "rt_z", "heading_error_z", "distance_z"),
                                                 type = fct_relevel(type, "repeated", "switch"),
                                                 valence = fct_relevel(valence, "univalent", "bivalent"),
                                                 cti = fct_relevel(cti, "long", "short"),
                                                 group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

p.switch_emmeans <- p.switch_emmeans + theme( legend.key.size = unit(0.3, "cm") )

# Save plot as pdf
pdf("./Figures/Executive Control/p.switch_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.switch_emmeans)
dev.off()

# Adjust legend size
facet_grid_def <- facet_grid(type ~ .id,
                             switch = "y",
                             labeller = labeller_def) 

# Switch bivalent short only
p.switch_emmeans_switch_bi_short <- func_plot_bar_facet( subset(emm_fac, type == "switch" & valence == "bivalent" & cti == "short") %>%
                                          mutate(.id = fct_relevel(.id, "rt_z", "heading_error_z", "distance_z"),
                                                 type = fct_relevel(type,  "switch"),
                                                 valence = fct_relevel(valence, "bivalent"),
                                                 cti = fct_relevel(cti,  "short"),
                                                 group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))


# Adjust legend size
p.switch_emmeans_switch_bi_short <- p.switch_emmeans_switch_bi_short + theme( legend.key.size = unit(0.3, "cm") )

# Save plot as pdf
pdf("./Figures/Executive Control/p.switch_emmeans_switch_bi_short.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats = FALSE) #in cm
print(p.switch_emmeans_switch_bi_short)
dev.off()
```
<!---BLOCK_LANDSCAPE_START--->
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 10, fig.height = 6, echo = FALSE, fig.cap = "Switch Task: Effect of bed rest on speed, accuracy, and efficiency on R+1. Data are means and SE adjusted for baseline, age, and sex."}
p.switch_emmeans
```
<!---BLOCK_LANDSCAPE_STOP--->
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 3, fig.height = 2.5, echo = FALSE, fig.cap = "Switch Task: Effect of bed rest on speed, accuracy, and efficiency on R+1. Data are means and SE adjusted for baseline, age, and sex."}
p.switch_emmeans_switch_bi_short
```
##Create Summary Combined plot 
```{r combined plot summary}
p.exec_comb <- plot_grid(p.dual_emmeans_dual, p.switch_emmeans_switch_bi_short, labels = c('a', 'b'), ncol = 2, nrow = 1) +
  theme(legend.key.size = unit(0.3, 'cm'))
```
```{r fig.id = "tsplot", fig.cap.style = "Image Caption", fig.width = 6, fig.height = 2.5, echo = FALSE, fig.cap = "Effect of bed rest on Executive Functions on R+1. (a) Psychological refractory period paradigm (Dual Task) showing speed, accuracy, and efficiency for dual task blocks. (b) Switching task showing speed, accuracy, and efficiency for mixed blocks. Data are means and SE adjusted for baseline, age, and sex."}
p.exec_comb
```
