---
title: "AGBRESA Extract Cognitive Data"
author: "A Stahn"
date: "11/08/2021"
output: html_document
---
```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Prepare Script
## Required Packages
```{r load required packages, message = FALSE}
library(knitr) # for kable
library(readxl) # read xls
library(DT) # Print table nicely in markdown
library(reshape2) # wide to long
library(plyr) # ldply
library(tidyverse) # for fct_relevel

library(lme4) # for adding mixed model functions to plot
library(lmerTest) # for adding mixed model functions to plot
library(nlme)
library(emmeans) # for adding mixed model marignal means and se to plot
library(qdapTools) # list_df2df(tbl_mm_fac_aov)

library(ggpubr) # for compare means, descriptives and theme_pubr
library(ggplot2)
library(ggsci)
library(scales)
library(cowplot) # for plot_grid, combine plots using cowplot
```
## Print Session Info
```{r print R and package versions}
print(sessionInfo())
```
## Themes for Plots
```{r create themes and correction factors}
# Correct ggplot2 pts and fonts
ggplot_factor_line <- ggplot2::.pt*72.27/96
ggplot_factor_font = 1.0

# Create project report theme
theme_report_white  <-  theme_pubr() + theme(
  axis.line = element_line(size = 0.5 / ggplot_factor_line,color="black"),
  axis.ticks = element_line(size = 0.5 / ggplot_factor_line, color="black"),
  axis.ticks.length = unit(0.2, "cm"), 
  text = element_text(size = 8 * ggplot_factor_font,
                      family="Helvetica",
                      colour="black"),
  axis.text.x=element_text(angle = 0, 
                           vjust = 0.5,
                           size = 8 * ggplot_factor_font,
                           family = "Helvetica",
                           colour = "black"), #face="bold"
  axis.text.y = element_text(angle = 0,
                            vjust=0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour="black"),
  axis.title.x = element_text(angle = 0,
                            vjust =0.5,
                            size= 8 * ggplot_factor_font,
                            family="Helvetica",
                            colour="black",
                            face="bold"),
  axis.title.y = element_text(angle = 90,
                            vjust = 0.5,
                            size= 8 * ggplot_factor_font,
                            family = "Helvetica",
                            colour = "black",
                            face = "bold") # face = "bold" 
  )
```
# Definition of Helper Functions 
## Descriptive Functions
```{r functions for descriptive stats}
# Function to compute descriptives
func_desc <- function(data, ...) {
  df_tmp <- df_demo[ , !names(df_demo) %in% c("age","height", "weight")]
  data <- merge(df_tmp, data, by = "id") #add demo
  data <- reshape2::melt( data, 
                              id.vars = names( Filter(is.factor, data) )
                              )
  groups <- enquos(...)
  
  result <- data %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      MEAN = mean(value, na.rm = T),
      SE = sd(value, na.rm = T) / sqrt(length(value) )
      )
  return(result)
}

func_bdc_correction <- function(data, ...) {

  df_tmp <- data %>%
    subset(time.f == "BDC-6" | time.f == "BDC-7" |time.f == "BDC-9") %>%
    group_by(group_3) %>%
    dplyr::summarise(
      mean_bdc_by_group = mean(MEAN, na.rm = T)
      )
  
  df_tmp <- merge(df_tmp, data, by = "group_3")
  df_tmp %>%
    mutate(MEAN_corr = case_when(time.f == "BDC-6" | time.f == "BDC-7" | time.f == "BDC-9" ~
                              MEAN-mean_bdc_by_group,
                            TRUE ~ MEAN)) %>%
    select( c(!mean_bdc_by_group & !MEAN) ) %>%
    rename(MEAN = MEAN_corr)
}
```
## Plot Functions
```{r functions for plots}
# Wrapper function for line plots, forwards to func_plot_line_facet
func_plot_line <- function(x) {ggplot(x, tmpaes_plot) + 
    theme_report_white +
    geom_line(position = pd) +
    geom_errorbar(tmpaes_errorbar,
                  width =.4, 
                  position = pd) +
    geom_point(position = pd,
               shape = 21,
               size = 2) + #shape = 21, size = 1, fill = "white"
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "Time", size = 10) +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 10))
  }

# Function for line plots, takes 'desc' as input
func_plot_line_facet <- function(x) {func_plot_line(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}

# Function for bar plots, forwards to func_plot_bar_facet
func_plot_bar <- function(x) {ggplot(x, tmpaes_plot) + theme_report_white +
    geom_hline(yintercept = 0,
               size = 0.3,
               linetype = "solid") +
    geom_errorbar(tmpaes_errorbar,
                 width = .4,
                  position = pd,
                  color = "black") +
    geom_bar(tmpaes_geombar, # separate by category
             stat = "identity", 
             position = pd,
             width = 1.0,
             color = "black") + # make it side-by-side
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "", x = "", size = 10) +
    guides(x = "none") +
    theme(legend.title = element_blank(),
          legend.text = element_text(size=8),
          axis.title.x = element_text(size = 10),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}

# Function for bar plots, takes 'desc*' as input
func_plot_bar_facet <- function(x) {func_plot_bar(x) +
    facet_grid_def +
    theme(strip.placement = "outside",
          strip.background = element_rect(color = "transparent",
                                          fill = "transparent", size = 1.5,
                                          linetype = "solid"),
          strip.text = element_text(size = 10,
                                    color = "black",
                                    face = "bold"),
          panel.spacing.y = unit(2, "lines"))
}
```
## Functions for Mixed Models
```{r functions for mixed models}
# Wrapper for appending bdc data as covariate
func_bdc_cov <- function(data, ...) {
  
  df_tmp <- subset(data, time.f != bdc)
  
  df_tmp_pre <- subset(data, time.f == bdc) %>%
    rename_at(vars(contains("_z")), ~ str_c("pre_", .)) %>%
    select("id" | is.numeric)
  
  df_tmp <- merge(df_tmp_pre, df_tmp, by = "id")
  droplevels(df_tmp)
  
  df_tmp <- merge(df_demo, df_tmp,by  = c("id")) 
}

func_bdc_cov_mult_all <- function(data, ...) {
  
  df_tmp <- subset(data, time.n > bdc )
  
  groups <- enquos(...)
  
  df_tmp_pre <- subset(data, time.n < (bdc+1) ) %>%
    
    group_by(!!!groups) %>%
    
    dplyr::summarise(
      rt_z = mean(rt_z, na.rm = T),
      acc_z = mean(acc_z, na.rm = T),
      eff_z = mean(eff_z, na.rm = T)
      ) %>%
    
    rename_at(vars(contains("_z")), ~ str_c("pre_", .))
    #select("id" | is.numeric)
  
  df_tmp <- merge(df_tmp_pre, df_tmp, by = c("id") )
  droplevels(df_tmp)
 
  df_tmp <- merge(df_demo[c(1,3,5:6)], df_tmp, by  = c("id")) 
}

# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_with_bdc_adj_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ pre_", i, model_mm),
                   REML = T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}

func_mm_fac_help <- function(dvList) {
  map(dvList, function(i) {
    lmerTest::lmer(paste0(i, " ~ ", model_mm),
                   REML = T,
                   data = df_tmp)
   }) %>% setNames(dvList) #add dvList names
}


# Function for creating mixed model tables, takes 'dvList'
func_tbl_aov <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[4] <- "df1"
  names(tbl_mm_fac_aov)[5] <- "df2"
  names(tbl_mm_fac_aov)[6] <- "F"
  names(tbl_mm_fac_aov)[7] <- "P"
  tbl_mm_fac_aov[c(5:6)] <- round(tbl_mm_fac_aov[c(5:6)], digits = 2) # Round
  tbl_mm_fac_aov[c(7)] <- round(tbl_mm_fac_aov[c(7)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}

# Function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f); also requires 'func_mm_fac_with_bdc_adj_help'
func_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

func_emm_fac <- function(x) {
  mm_fac <- func_mm_fac_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}


# Helper function contrasts emmeans, takes 'dvList'; also requires 'func_mm_fac_with_bdc_adj_help'
func_contrasts_emm_fac_with_bdc_adj <- function(x) {
  mm_fac <- func_mm_fac_with_bdc_adj_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

func_contrasts_emm_fac <- function(x) {
  mm_fac <- func_mm_fac_help(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust = "none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer=T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}


# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac_with_bdc_adj <- function(dvList) {
  tmp <- func_contrasts_emm_fac_with_bdc_adj(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}

# Function for creating table of contrasts emmeans, takes 'dvList', and requires 'func_contrasts_emm_fac_with_bdc_adj'
func_tbl_contr_emm_fac <- function(dvList) {
  tmp <- func_contrasts_emm_fac(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}


# nlme
# Wrapper for mixed models, takes 'dvList', requires 'model_mm', e.g., model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " * cond.f", " + (1|id)" )
func_mm_fac_help_nlme <- function(dvList) {
  map(dvList, function(i) {
    f <- formula(paste(i, pred, sep = "~"))
    mm <- lme(fixed = f,
              random = ~ 1 | id,
              data = df_tmp)
    mm$call$fixed <- f
    mm}) %>% setNames(dvList)
}

# Helper functions for creating mixed model tables, takes 'dvList'
func_tbl_aov_nlme <- function(x) {
  tbl_mm_fac_aov <- list_df2df(tbl_mm_fac_aov)
  names(tbl_mm_fac_aov)[2] <- "df1"
  names(tbl_mm_fac_aov)[3] <- "df2"
  names(tbl_mm_fac_aov)[4] <- "F"
  names(tbl_mm_fac_aov)[5] <- "P"
  tbl_mm_fac_aov[c(4)] <- round(tbl_mm_fac_aov[c(4)], digits = 2) # Round
  tbl_mm_fac_aov[c(5)] <- round(tbl_mm_fac_aov[c(5)], digits = 3) # Round
  return(tbl_mm_fac_aov)
}


# Helper function emmeans, takes 'dvList'; requires to define 'model', e.g., model <- c(~ time.f * group_3 * cond.f)
func_emm_fac_nlme <- function(x) {
  mm_fac <- func_mm_fac_help_nlme(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  emm_fac_ <- lapply(emm_fac, data.frame)
  table_emm_fac_df <- ldply(emm_fac_, data.frame) #create df
  table_emm_fac_df_raw <- table_emm_fac_df
  table_emm_fac_df_raw$.id <- as.factor(as.character(table_emm_fac_df_raw$.id ))
  rm(emm_fac_)
  return(table_emm_fac_df_raw)
}

# Function for contrasts, requires 'func_mm_fac_help'
func_contrasts_emm_fac_nlme <- function(x) {
  mm_fac <- func_mm_fac_help_nlme(dvList)
  emm_fac <- lapply(mm_fac, function(mm_fac) emmeans::emmeans(mm_fac, model_emmeans, lmer.df = "satterthwaite"))
  contrasts_mm_fac <- lapply(emm_fac, function(emm_fac) contrast(emm_fac, contrast_type,
                                                                         by = factors,
                                                                         lmer.df = "satterthwaite",
                                                                         adjust="none"))
  contrasts_mm_fac <- lapply(contrasts_mm_fac, summary, infer = T) #add adj confidence intervals (adjusted if adjustment method is selected: https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html)
  contrasts_mm_fac_ <- lapply(contrasts_mm_fac, data.frame) #create df
  contrasts_mm_fac_df <- ldply(contrasts_mm_fac_, data.frame) #create df
  rm(contrasts_mm_fac_)
  return(contrasts_mm_fac_df)
}

# Helper function contrasts emmeans, takes 'dvList', and requires func_contrasts_emm_fac_nlme
func_tbl_contr_emm_fac_nlme <- function(dvList) {
  tmp <- func_contrasts_emm_fac_nlme(dvList)
  tmp[ncol(tmp)] <- round(tmp[ncol(tmp)], digits = 3) #round
  tmp[ncol(tmp)-1] <- round(tmp[ncol(tmp)-1], digits = 2) #round
  tmp[ncol(tmp)-2] <- round(tmp[ncol(tmp)-2], digits = 2) #round
  tmp[ncol(tmp)-3] <- round(tmp[ncol(tmp)-3], digits = 2) #round
  tmp[ncol(tmp)-4] <- round(tmp[ncol(tmp)-4], digits = 1) #round
  tmp[ncol(tmp)-5] <- round(tmp[ncol(tmp)-5], digits = 2) #round
  tmp[ncol(tmp)-6] <- round(tmp[ncol(tmp)-6], digits = 2) #round
  tmp$CI <- paste0("(",tmp$lower.CL,"," ,tmp$upper.CL,")")
  tmp$CI <- gsub( ",", ", ", tmp$CI ) 
  tmp$CI <- paste0(tmp$estimate," " ,tmp$CI)
  tmp <- tmp[-c(ncol(tmp)-3,
                ncol(tmp)-4,
                ncol(tmp)-6,
                ncol(tmp)-7)]
  colnames(tmp)[ncol(tmp)] <- "Mean (95%CI)"
  colnames(tmp)[ncol(tmp)-1] <- "P (unadjusted)"
  colnames(tmp)[ncol(tmp)-2] <- "t"
  colnames(tmp)[2] <- "Contrast"
  return(tmp)
}
```
## Load Data
```{r load data}
#  Demographics
df_demo <- read_excel("./Data/Data Demographics.xlsx", sheet = "Data Demo")
df_demo[c(1:5)] <- lapply(df_demo[c(1:5)], as.factor)

# Spatial Cognition 1

# SUT
df_sut <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data SUT prout")
df_sut[c(1:2,6)] <- lapply(df_sut[c(1:2,6)], as.factor)

df_sut_45 <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data SUT prout 45")
df_sut_45[c(1:2,6)] <- lapply(df_sut_45[c(1:2,6)], as.factor)

# PTO
df_pto <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data PTO prout")
df_pto[c(1:2,7)] <- lapply(df_pto[c(1:2,7)], as.factor)

df_pto_5 <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data PTO prout 5")
df_pto_5[c(1:2,7)] <- lapply(df_pto_5[c(1:2,7)], as.factor)
df_pto_5[c(1:2,7)] <- lapply(df_pto_5[c(1:2,7)], as.factor)

# 4MTN
df_4mtn <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data 4MTN prout")
df_4mtn[c(1:2,6)] <- lapply(df_4mtn[c(1:2,6)], as.factor)

# NAVIS 2D
df_navis_2d <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data NAVIS 2D prout")
df_navis_2d[c(1:2,8)] <- lapply(df_navis_2d[c(1:2,8)], as.factor)

df_navis_2d_night <- read_excel("./Data/Data Spatial Cognition 1 prout.xlsx", sheet = "Data NAVIS 2D prout Night")
df_navis_2d_night[c(1:2,8)] <- lapply(df_navis_2d_night[c(1:2,8)], as.factor)

# Spatial Cognition 2

# SOT
df_sot <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data SOT prout")
df_sot[c(1:2,6)] <- lapply(df_sot[c(1:2,6)], as.factor)

# Cognitive Mapping
df_cogmap <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data Cognitive Mapping prout")
df_cogmap[c(1:2,6)] <- lapply(df_cogmap[c(1:2,6)], as.factor)

# Water Maze
df_wm <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data WM prout")
df_wm[c(1:2,7)] <- lapply(df_wm[c(1:2,7)], as.factor)


# Plus Maze
df_pm <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data PM prout")
df_pm[c(1:2,6)] <- lapply(df_pm[c(1:2,6)], as.factor)

# Navigation Strategy
df_navstrat <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data Navstrat Avr prout")
df_navstrat[c(1:2,6)] <- lapply(df_navstrat[c(1:2,6)], as.factor)

df_navstrat_same <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data Navstrat Same prout")
df_navstrat_same[c(1:2,6)] <- lapply(df_navstrat_same[c(1:2,6)], as.factor)

df_navstrat_diff <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data Navstrat Diff prout")
df_navstrat_diff[c(1:2,6)] <- lapply(df_navstrat_diff[c(1:2,6)], as.factor)

# NAVIS VR
df_navis_vr <- read_excel("./Data/Data Spatial Cognition 2 prout.xlsx", sheet = "Data NAVIS VR prout")
df_navis_vr[c(1:2,8)] <- lapply(df_navis_vr[c(1:2,8)], as.factor)

# Executive Control
# Dual Task
df_dual <- read_excel("./Data/Data Executive Control prout.xlsx", sheet = "Data Dual prout")
df_dual[c(1:2,6)] <- lapply(df_dual[c(1:2,6)], as.factor)

# Switch Task
df_switch <- read_excel("./Data/Data Executive Control prout.xlsx", sheet = "Data Switch prout")
df_switch[c(1:2,6)] <- lapply(df_switch[c(1:2,6)], as.factor)

# Cognition
df_cognition <- read_excel("./Data/Data Cognition Avr prout.xlsx", sheet = "Data Cognition Avr prout")
df_cognition[c(1:2)] <- lapply(df_cognition[c(1:2)], as.factor)

```
# Spatial Cognition Battery 1
## Overall score
```{r overall score spacog_1}
# Define primary outcomes
df_pto_v1 <- df_pto[-c(3)] 
df_pto_v2 <- df_pto[-c(5)] 
colnames(df_pto_v2)[3] <- "acc_z"
df_pto_v2$eff_z <- (df_pto_v2$rt_z + df_pto_v2$acc_z) / 2
  
df_navis_2d_v1 <- df_navis_2d[-c(5,7)] 
colnames(df_navis_2d_v1)[4] <- "acc_z"
colnames(df_navis_2d_v1)[5] <- "eff_z"

df_navis_2d_v2 <- df_navis_2d[-c(4,6)] 
colnames(df_navis_2d_v2)[4] <- "acc_z"
colnames(df_navis_2d_v2)[5] <- "eff_z"

# Combine tasks in one variable
df_spacog_1 <- rbind(df_4mtn, df_sut, df_pto_v1, df_navis_2d_v2)
```
## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline spacog_1}
# Mean across tasks
desc <- func_desc(df_spacog_1, group_3, time.f, variable)

# Plot desc
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels)

facet_grid_def <- facet_grid(variable ~.,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.spacog_1_desc <- func_plot_line_facet(desc %>%
                                     mutate(time.f = fct_relevel(time.f, "BDC-3", "HDT2", "HDT30", "HDT59", "R+12"),
                                            variable = fct_relevel(variable, "rt_z","acc_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.spacog_1_desc <- p.spacog_1_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.spacog_1_desc <- p.spacog_1_desc + theme(legend.key.size = unit(0.3, "cm"))

```

## Mixed Model Time x Group Interaction 
```{r mixed model for time x group spacog_1}
# Mean across tasks
df_tmp <- func_desc(df_spacog_1, id, group_3, time.f, variable)
df_tmp <- df_tmp[-c(2,6)]
df_tmp <- reshape2::dcast(df_tmp, id + time.f ~ variable, value.var = "MEAN")

# Add baseline as cov
bdc <- "BDC-3"
df_tmp <-  func_bdc_cov(df_tmp)

# Select dep vars
dvList <- c("rt_z","acc_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Time x Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_spacog_1 <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 2. Mixed Model Summary for Spatial Cognition Battery 1.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_spacog_1, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Comparing Groups at Each Time Point During Bed Rest
```{r contrasts for groups by time spacog_1}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c("time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Time <- rep ( c("HDT2", rep("", tmp_n_time),
                                     "HDT30", rep("", tmp_n_time),
                                     "HDT59", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList) )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Ttble for contrasts
tbl_contr_emm_fac_df_spacog_1 <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 4:6)]
```
#### Table 3. Mixed Model Group Contrasts for Spatial Cognition Battery 1.
```{r echo = FALSE}
# Print table 
datatable(tbl_contr_emm_fac_df_spacog_1, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns = c("df", "t"), digits = 1)
```

## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot emmeans for groups by time spacog_1}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~.id ,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.spacog_1_emmeans <- func_plot_line_facet(emm_fac %>%
                                        mutate(time.f = fct_relevel(time.f, "BDC-3", "HDT2", "HDT30", "HDT59", "R+12"),
                                               .id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                               group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.spacog_1_emmeans <- p.spacog_1_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.spacog_1_emmeans <- p.spacog_1_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group spacog_1}
# Drop recovery
df_tmp <- subset(df_tmp, time.f != "R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","acc_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_spacog_1_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 4. Mixed Model Summary testing the Main Effect of Group for Spatial Cognition Battery 1.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_spacog_1_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```
## Contrasts for Comparing Groups
```{r contrasts for groups spacog_1}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 1),
                                   "Accuracy", rep("", 1),
                                   "Efficiency", rep("", 1))
#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_spacog_1_main <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 5. Mixed Model Contrasts Comparing Groups for Spatial Cognition Battery 1.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_spacog_1_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns = c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Comparing Groups
```{r plot groups spacog_1}
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(.id ~ .,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.spacog_1_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                            mutate(
                                                   .id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                                   group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) 
# Adjust legend size
p.spacog_1_emmeans_main <- p.spacog_1_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
## Create Combined plot 
```{r plot combined spacog_1}
# Combine plot 
p.spacog_1_comb <- plot_grid(p.spacog_1_desc, p.spacog_1_emmeans_main + rremove("x.text") + theme( strip.text.y = element_blank() ),
                        labels = c("a", "b"),
                        ncol = 2, nrow = 1,
                        rel_widths = c(1.9, 1.1))

# Adjust legend size
p.spacog_1_comb <- p.spacog_1_comb + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Spatial Cognition 1/p.spacog_1_comb.pdf",
    width = 30/2.54, 
    height = 20/2.54,
    useDingbats = FALSE) #in cm
print(p.spacog_1_comb)
dev.off()
```
#### Figure 1. Spatial Cognition Battery 1: (a) Time course of speed, precision, and efficiency before, during, and after bed rest. (b) Main effect of bed rest. Data are means and SD adjusted for baseline.
```{r, echo = FALSE, fig.width = 6, fig.height = 8, fig.cap = ""}
print(p.spacog_1_comb)
```

# Spatial Cognition Battery 2
## Overall score
```{r overall score spacog_2}
# Define primary outcomes
df_wm_v1 <- df_wm[-c(4)] 
colnames(df_wm_v1)[4] <- "acc_z"
df_wm_v2 <- df_wm[-c(4)] 
colnames(df_wm_v2)[4] <- "acc_z"
df_wm_v2$eff_z <- (df_wm_v2$rt_z + df_wm_v2$acc_z) / 2

df_navstrat_same 
df_navstrat_diff
df_navstrat

df_navis_vr_v1 <- df_navis_vr[-c(5,7)] 
colnames(df_navis_vr_v1)[4] <- "acc_z"
colnames(df_navis_vr_v1)[5] <- "eff_z"

df_navis_vr_v2 <- df_navis_vr[-c(4,6)] 
colnames(df_navis_vr_v2)[4] <- "acc_z"
colnames(df_navis_vr_v2)[5] <- "eff_z"

# Combine tasks in one variable
df_spacog_2 <- rbind(df_sot, df_cogmap, df_wm_v1, df_navstrat, df_navis_vr_v1)
```
#### Mixed Model Comparing Groups
```{r echo = FALSE}
# Drop BDC
df_tmp <- subset(df_spacog_2, time.f != "BDC-6" &  time.f != "R+12")
df_tmp <- droplevels(df_tmp)

# Mean across tasks
df_tmp <- func_desc(df_tmp, id, group_3, variable)
df_tmp <- df_tmp[-c(5)]
df_tmp <- reshape2::dcast(df_tmp, id  +  group_3 ~ variable, value.var = "MEAN")

# Mixed Models
# Add groups
df_tmp <- merge(df_demo[c(1,3,5,6)], df_tmp, by = c("id", "group_3"))

# Select dep vars
dvList <- c("rt_z", "acc_z", "eff_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)

tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_spacog_2 <- cbind(Variable, Parameter, tbl_mm_fac_aov_df)
tbl_mm_fac_aov_df_spacog_2 <- tbl_mm_fac_aov_df_spacog_2[-c(3)]
```

#### Table 6. Mixed Model Summary for Spatial Cognition Battery 2.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_spacog_2, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between groups spacog_2}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)


# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 2),
                                   "Accuracy", rep("", 2),
                                   "Efficiency", rep("", 2))


# Table for contrasts
tbl_contr_emm_fac_df_spaccog_2 <- tbl_contr_emm_fac_df[c(7,2,6,3:5)]
```
#### Table 7. Mixed Model Group Contrasts for Spatial Cognition Battery 2.
```{r echo = FALSE}
# print table
datatable(tbl_contr_emm_fac_df_spaccog_2, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups spacog_2}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "acc_z","eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.spacog_2_emmeans <- func_plot_bar_facet(emm_fac %>%
                                        mutate(.id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.spacog_2_emmeans <- p.spacog_2_emmeans + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Executive Control/p.spacog_2_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats=FALSE) #in cm
print(p.spacog_2_emmeans)
dev.off()
```
#### Figure 2. Spatial Cognition Battery 2: Effects of Bed Rest on Speed, Accuracy, and Efficiency after Bed Rest. Data are means and SE.
```{r, echo = FALSE, fig.width = 5, fig.height = 4, fig.cap = ""}
print(p.spacog_2_emmeans)
```
# Executive Control
## Overall score
```{r overall score exe_ctrl}
# Combine tasks in one variable
df_exe_ctrl <- rbind(df_switch, df_dual)
```

## Comparing Groups
```{r echo = FALSE}
# Drop BDC
df_tmp <- subset(df_exe_ctrl, time.f != "BDC-6")
df_tmp <- droplevels(df_tmp)

# Mean across tasks
df_tmp <- func_desc(df_tmp, id, group_3, variable)
df_tmp <- df_tmp[-c(5)]
df_tmp <- reshape2::dcast(df_tmp, id  +  group_3 ~ variable, value.var = "MEAN")

# Mixed Models
# Add groups
df_tmp <- merge(df_demo[c(1,3,5,6)], df_tmp, by = c("id", "group_3"))

# Select dep vars
dvList <- c("rt_z", "acc_z", "eff_z")

# Select predictors
pred <- c("sex + age + group_3")

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_help_nlme(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov_nlme(dvList)

tbl_mm_fac_aov_df <- tbl_mm_fac_aov_df[-c(1, 5, 9),]

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_exe_ctrl <- cbind(Variable, Parameter, tbl_mm_fac_aov_df)
tbl_mm_fac_aov_df_exe_ctrl <- tbl_mm_fac_aov_df_exe_ctrl[-c(3)]
```

#### Table 8. Mixed Model Summary for Executive Control Tasks.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_exe_ctrl, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Group Comparisons
```{r contrasts between groups exe_ctrl}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_nlme(dvList)


# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 2),
                                   "Accuracy", rep("", 2),
                                   "Efficiency", rep("", 2))


# Table for contrasts
tbl_contr_emm_fac_df_exe_ctrl <- tbl_contr_emm_fac_df[c(7,2,6,3:5)]
```
#### Table 9. Mixed Model Group Contrasts for Executive Control Tasks.
```{r echo = FALSE}
# print table
datatable(tbl_contr_emm_fac_df_exe_ctrl, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns=c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns=c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Group Comparisons
```{r plot emmeans by groups exe_ctrl}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_nlme(dvList) 

# Plot emmeans 
# Define aes for func_plot
tmpaes_plot <- aes(x = group_3, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z", "acc_z","eff_z")

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~ .id,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.99)
p.exe_ctrl_emmeans <- func_plot_bar_facet(emm_fac %>%
                                        mutate(.id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                          group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Adjust legend size
p.exe_ctrl_emmeans <- p.exe_ctrl_emmeans + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Executive Control/p.exe_ctrl_emmeans.pdf",
    width = 5/2.54,
    height = 8/2.54,
    useDingbats=FALSE) #in cm
print(p.exe_ctrl_emmeans)
dev.off()
```
#### Figure 3. Executive Control Tasks: Effects of Bed Rest on Speed, Accuracy, and Efficiency after Bed Rest. Data are means and SE.
```{r, echo = FALSE, fig.width = 5, fig.height = 4, fig.cap = ""}
print(p.exe_ctrl_emmeans)
```
# Cognition
## Overall score
```{r overall score cognition}
df_cognition
```

## Plot Time Course adjusted for Baseline 
```{r plot time course adjusted for baseline cognition}
# Plot arithmetic means
# Mean across tasks
desc <- func_desc(df_cognition, group_3, time.f, variable)

# Shift mean within groups to reflect a pre-HDT baseline performance of 0 (zero) (To reflect the analytical approach (adjusting for baseline performance).
desc <- func_bdc_correction(desc)

# Plot desc
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = MEAN,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = MEAN-SE, 
                    ymax = MEAN+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(variable = new_labels)

facet_grid_def <- facet_grid(variable ~.,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.5)
p.cognition_desc <- func_plot_line_facet(desc %>%
                                     mutate(time.f = fct_relevel(time.f, "BDC-9", "BDC-7", "BDC-6", "HDT1", "HDT3", "HDT5","HDT14", "HDT28", "HDT42", "HDT57", "R+1", "R+5", "R+12"),
                                       variable = fct_relevel(variable, "rt_z","acc_z", "eff_z"),
                                            group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.cognition_desc <- p.cognition_desc + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.cognition_desc <- p.cognition_desc + theme(legend.key.size = unit(0.3, "cm"))
```

## Mixed Model Time x Group Interaction 
```{r mixed model for time x group cognition}
# Create baseline data
# relabel time.f
df_cognition$time.n <- plyr::revalue(df_cognition$time.f, c("BDC-9" = "01", "BDC-7" = "02", "BDC-6" = "03", "HDT1" = "04", "HDT3" = "05", "HDT5" = "06", "HDT14" = "07", "HDT28" = "08", "HDT42" = "09", "HDT57" = "10", "R+1" = "11", "R+5" = "12", "R+12" = "13"))
df_cognition <- df_cognition[c(1:2,6, 3:5)]
df_cognition$time.n <- as.character((df_cognition$time.n))
df_cognition$time.n <- as.numeric((df_cognition$time.n))

# Define BDC sessions (number indicates last bdc sessions based on time.n)
bdc <- 3
df_tmp <- func_bdc_cov_mult_all(df_cognition, id)

# Select dep vars
dvList <- c("rt_z","acc_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + time.f",  " * group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table 
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Time",
  "Group",
  "Time x Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_cognition <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 10. Mixed Model Summary for Cognition Battery.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_cognition, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```

## Contrasts for Comparing Groups at Each Time Point During Bed Rest
```{r contrasts for groups by time cognition}
# Contrasts
# Define model for contrasts
model_emmeans <- ~ time.f * group_3

# Define contrasts
contrast_type <- "pairwise"
factors <- c("time.f")

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tmp_n_dvs <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) -1
tmp_n_cond <- length(levels(tbl_contr_emm_fac_df$Contrast)) * 
  length(levels(tbl_contr_emm_fac_df$time.f)) - 1
tmp_n_time <- length(levels(tbl_contr_emm_fac_df$Contrast)) - 1


tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", tmp_n_dvs),
                                   "Accuracy", rep("", tmp_n_dvs),
                                   "Efficiency", rep("", tmp_n_dvs))

tbl_contr_emm_fac_df$Time <- rep ( c("HDT1", rep("", tmp_n_time),
                                     "HDT3", rep("", tmp_n_time),
                                     "HDT5", rep("", tmp_n_time),
                                     "HDT14", rep("", tmp_n_time),
                                     "HDT28", rep("", tmp_n_time),
                                     "HDT42", rep("", tmp_n_time),
                                     "HDT57", rep("", tmp_n_time),
                                     "R+1", rep("", tmp_n_time),
                                     "R+5", rep("", tmp_n_time),
                                     "R+12", rep("", tmp_n_time)),
                                   length(dvList)/3 )

#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_df_cognition <- tbl_contr_emm_fac_df[c(8:9, 2, 7, 4:6)]
```
#### Table 11. Mixed Model Group Contrasts for Cognition Battery.
```{r echo = FALSE}
# Print table 
datatable(tbl_contr_emm_fac_df_cognition, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns = c("df", "t"), digits = 1)
```

## Plot Estimated Marignal Means To Show Time Course for Each Group
```{r plot emmeans for groups by time cognition}
# Define model for emmeans
model_emmeans <- ~ time.f * group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList) 

# Plot emmeans 
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = time.f, y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = time.f,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(~.id ,
                             switch = "y",
                             labeller = labeller_def) 

# Draw plot
pd <- position_dodge(0.3)
p.cognition_emmeans <- func_plot_line_facet(emm_fac %>%
                                        mutate(time.f = fct_relevel(time.f, "HDT1", "HDT3", "HDT5","HDT14", "HDT28", "HDT42", "HDT57", "R+1", "R+5", "R+12"),
                                               .id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                               group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG")))

# Add zero line
p.cognition_emmeans <- p.cognition_emmeans + geom_hline(yintercept = 0, size = 0.3, linetype = "dotted")

# Adjust legend size
p.cognition_emmeans <- p.cognition_emmeans + theme(legend.key.size = unit(0.3, "cm"))
```
## Mixed Model for Main Effect of Bed Rest (excluding BDC)
```{r mixed model for main effect group cognition}
# Drop recovery
df_tmp <- subset(df_tmp, time.f != "R+12") # Drop baseline
df_tmp <- droplevels(df_tmp)

# Select dep vars
dvList <- c("rt_z","acc_z", "eff_z")

# Define model
model_mm <- paste0(" + sex"," + age", " + group_3", " + (1|id)" )

# Run mixed models
tbl_mm_fac_aov <- sapply(func_mm_fac_with_bdc_adj_help(dvList), anova, simplify = FALSE, USE.NAMES = TRUE) 

# ANOVA table
tbl_mm_fac_aov_df <- func_tbl_aov(dvList)

# Helper functions for parameter definition in mixed model tables, takes 'dvList'
Parameter_func <- function(dvList){
  rep(c(
  "Baseline",
  "Sex",
  "Age",
  "Group"),
                 length(dvList))
}

# Add variables
Parameter <- Parameter_func(dvList)
blanks <- rep("", length(Parameter) / length(dvList) - 1)
Variable <- c("Speed", blanks,"Accuracy", blanks, "Efficiency", blanks)
tbl_mm_fac_aov_df_cognition_main <- cbind(Variable, Parameter, tbl_mm_fac_aov_df[c(4:7)])
```
#### Table 12. Mixed Model Summary testing the Main Effect of Group for Cognition Battery.
```{r echo = FALSE}
# Print table
datatable(tbl_mm_fac_aov_df_spacog_1_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P"), digits = 3) %>%
  formatRound(columns = c("df2", "F"), digits = 1)
```
## Contrasts for Comparing Groups
```{r contrasts for groups cognition}
# Define model for emmeans
model_emmeans <- ~ group_3

# Run emmeans
emm_fac <- func_emm_fac_with_bdc_adj(dvList)

# Contrasts
# Define model for contrasts
model_emmeans <- ~ group_3

# Define contrasts
contrast_type <- "trt.vs.ctrl"
factors <- c()

# Run contrasts
tbl_contr_emm_fac_df <- func_tbl_contr_emm_fac_with_bdc_adj(dvList)

# Create vars to make nice table
tbl_contr_emm_fac_df$Variable <- c("Speed", rep("", 1),
                                   "Accuracy", rep("", 1),
                                   "Efficiency", rep("", 1))
#table_contrasts_emm_fac_by_time_df$Contrast <- rep(c("cAG vs. CTRL","iAG vs. CTRL", "cAG vs. iAG"), length(dvList))

# Table for contrasts
tbl_contr_emm_fac_cognition_main <- tbl_contr_emm_fac_df[c(7, 2, 6, 3:5)]
```
#### Table 5. Mixed Model Contrasts Comparing Groups for Cognition Battery.
```{r echo = FALSE}
# Print table
datatable(tbl_contr_emm_fac_cognition_main, 
          rownames = FALSE, filter = "top",
          options = list(pageLength = 50, 
                         scrollX = T)) %>%
  formatRound(columns = c("P (unadjusted)"), digits = 3) %>%
  formatRound(columns = c("df", "t"), digits = 1)
```
## Plot Estimated Marignal Means for Comparing Groups
```{r plot groups cognition}
# New facet label names for variable
new_labels <- c("Speed","Accuracy","Efficiency")
names(new_labels) <- c("rt_z","acc_z", "eff_z")

# Define aes for func_plot
tmpaes_plot <- aes(x = contrast,
                   y = emmean,
                   group = group_3,
                   fill = group_3,
                   color = group_3)

tmpaes_errorbar <- aes(x = group_3,
                    ymin = emmean-SE, 
                    ymax = emmean+SE)

tmpaes_geombar <- aes(x = group_3,
                    y = emmean, 
                    fill=group_3)

# Define labels for func_plot_line_facet
labeller_def <- labeller(.id = new_labels)

facet_grid_def <- facet_grid(.id ~.,
                             switch = "y",
                             scales = "free",
                             labeller = labeller_def) 

# Draw Plot 
pd <- position_dodge(0.99)
p.cognition_emmeans_main <- func_plot_bar_facet(emm_fac %>%
                                            mutate(
                                                   .id = fct_relevel(.id, "rt_z","acc_z", "eff_z"),
                                                   group_3 = fct_relevel(group_3, "CTRL", "cAG", "iAG"))) 
# Adjust legend size
p.cognition_emmeans_main <- p.cognition_emmeans_main + theme(legend.key.size = unit(0.3, "cm"))
```
## Create Combined plot 
```{r plot combined cognition}
# Combine plot 
p.cognition_comb_all <- plot_grid(p.cognition_desc, p.cognition_emmeans_main + rremove("x.text") + theme( strip.text.y = element_blank() ),
                        labels = c("a", "b"),
                        ncol = 2, nrow = 1,
                        rel_widths = c(2.3, 0.7))

# Adjust legend size
p.cognition_comb_all <- p.cognition_comb_all + theme(legend.key.size = unit(0.3, "cm"))

# Save plot as pdf
pdf("./Figures/Cognition/p.cognition_comb_all.pdf",
    width = 10/2.54, 
    height = 12/2.54,
    useDingbats = FALSE) #in cm
print(p.cognition_comb_all)
dev.off()
```
#### Figure 3.Cognition Battery 1: (a) Time course of speed, precision, and efficiency before, during, and after bed rest. (b) Main effect of bed rest. Data are means and SD adjusted for baseline.
```{r, echo = FALSE, fig.width = 10, fig.height = 8, fig.cap = ""}
print(p.cognition_comb_all)
```
