---
title: "AGBRESA Preprocess MRI"
author: "A Stahn"
date: "10/25/2021"
output: html_document
---
# Prepare Script
## Required Packages
```{r load required packages, message = FALSE}
library(readxl)#read xls
library(openxlsx) #save tables
library(plyr) #means across subjects and groups, change scores
library(dplyr) #distinct function
library(tidyverse)
```
## Print Session Info
```{r print R and package versions}
print(sessionInfo())
```
## Functions
```{r function for preprocessing}
# Preprocessing function blood
func_clean_var <- function(x){
  x$time.f <- x$file
  x$time.f <- gsub("AGBR-", "", x$time.f)
  x$time.f <- gsub( "-AS.*$", "", x$time.f ) #extract everythign after -AS from start
  x$time.f <- gsub('(.*)-\\w+', '\\1', x$time.f) #delete everyhting after last underscore
  x$id <- x$file
  x$id <- gsub("AGBR-", "", x$id)
  x$id <- gsub( "-AS.*$", "", x$id )
  x$id <- gsub(".*-","",x$id)
  x$tod <- x$file
  x$tod <- gsub("AGBR-", "", x$tod)
  x$tod <- gsub(".{3}$", "", x$tod)
  x$tod  <- gsub( "^*.-", "", x$tod  ) #delete everything before _
  x$tod  <- gsub(".*-","",x$tod)
  x$tod  <- gsub("AS","1",x$tod)
  x <- x[-c(1)]
  return(x)
}

# Preprocessing function cortisol
func_clean_var_cort <- function(x){
  x$time.f <- x$file
  x$time.f <- gsub("AGBR-", "", x$time.f)
  x$time.f <- gsub( "-AS.*$", "", x$time.f ) #extract everythign after -AS from start
  x$time.f <- gsub('(.*)-\\w+', '\\1', x$time.f) #delete everyhting after last underscore
  x$id <- x$file
  x$id <- gsub("AGBR-", "", x$id)
  x$id <- gsub( "-AS.*$", "", x$id )
  x$id <- gsub(".*-","",x$id)
  x$tod <- x$file
  x$tod <- gsub("AGBR-", "", x$tod)
  x$tod <- gsub("-Sal", "", x$tod)
  x$tod  <- gsub( "^*.-", "", x$tod  ) #delete everything before _
  x$tod  <- gsub(".*-","",x$tod)
  x$tod  <- gsub("AS","1",x$tod)
  x <- x[-c(1)]
  return(x)
}

# Helper function for bdc mean and sd, forward to 'func_z'
func_bdc <- function(x) (x %>%
  filter(!!!bdc) %>% # requires input as cat
  group_by(variable) %>%
  dplyr::summarize(
    mean_bdc = mean(value, na.rm=T),
    sd_bdc = sd(value, na.rm=T)
    )
  )

# Function for z scores, requires 'func_bdc'
func_z <- function(x) {
  tmp <- reshape2::melt(x, id.vars = id_vars) 
  #tmp <- df_lc
  dat_bdc <- func_bdc(tmp)
  tmp <- merge(tmp, dat_bdc, by ="variable")
  tmp$z <- (tmp$value - tmp$mean_bdc) / tmp$sd_bdc
  tmp$variable <- paste(tmp$variable, "z", sep="_")
  tmp_id_var <- paste(id_vars, collapse = "+")
  id_vars_dep <- paste(tmp_id_var, "~ variable" )
  tmp <- reshape2::dcast(tmp, id_vars_dep, value.var = "z")
  return(tmp)
}

```
# Load and Preprocess rsfMRI Data
```{r rsfmri AGBRESA}
# rsfmri
# AGpoolvsControlT1T3
# Read data
df_rsfrmi <- read_excel("/Users/astahn/Publications/AGBRESA/Data/rsfMRI/NBS_AGBRESA_posInteraction clean.xlsx", sheet = "AGpoolvsControlT1T3")

df_rsfrmi$id <- df_rsfrmi$subjs
df_rsfrmi$id <- gsub( "'", "", df_rsfrmi$id )
df_rsfrmi$id <- gsub( "AG_ST_", "", df_rsfrmi$id )

df_rsfrmi$id <- gsub( "_.*$", "", df_rsfrmi$id ) # delete everything before _1

df_rsfrmi$time.f <- df_rsfrmi$subjs
df_rsfrmi$time.f <- gsub( "'", "", df_rsfrmi$time.f )
df_rsfrmi$time.f <- gsub( "^.*_", "", df_rsfrmi$time.f ) # delete everything before_

# Rearrange
names(df_rsfrmi)
df_rsfrmi <- df_rsfrmi[c(8,9,4:7)]

# Rename columns
colnames(df_rsfrmi)[3] <- "meanFC_th3.0"
colnames(df_rsfrmi)[4] <- "meanFC_th3.1"
colnames(df_rsfrmi)[5] <- "meanFC_th3.2"
colnames(df_rsfrmi)[6] <- "meanFC_th3.8"

# Assign df
df_rsfrmi_ag_ctrl <- df_rsfrmi

# Convert var type
df_rsfrmi_ag_ctrl[c(1:2)] <- lapply(df_rsfrmi_ag_ctrl[c(1:2)], as.factor)
df_rsfrmi_ag_ctrl <- as_tibble(df_rsfrmi_ag_ctrl)

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_rsfrmi_ag_ctrl_z <- func_z(df_rsfrmi_ag_ctrl)
df_rsfrmi_ag_ctrl_z <- as_tibble(df_rsfrmi_ag_ctrl_z)

# cAGvsControl
# Read data
df_rsfrmi <- read_excel("/Users/astahn/Publications/AGBRESA/Data/rsfMRI/NBS_AGBRESA_posInteraction clean.xlsx", sheet = "cAGvsControl")

df_rsfrmi$id <- df_rsfrmi$subjs
df_rsfrmi$id <- gsub( "'", "", df_rsfrmi$id )
df_rsfrmi$id <- gsub( "AG_ST_", "", df_rsfrmi$id )
df_rsfrmi$id <- gsub( "_.*$", "", df_rsfrmi$id ) #delete everything before _1

df_rsfrmi$time.f <- df_rsfrmi$subjs
df_rsfrmi$time.f <- gsub( "'", "", df_rsfrmi$time.f )
df_rsfrmi$time.f <- gsub( "^.*_", "", df_rsfrmi$time.f ) # delete everything before_

# Rearrange
names(df_rsfrmi)
df_rsfrmi <- df_rsfrmi[c(8,9,4:7)]

# Rename columns
colnames(df_rsfrmi)[3] <- "meanFC_th3.0_3.2"
colnames(df_rsfrmi)[4] <- "meanFC_th3.3"
colnames(df_rsfrmi)[5] <- "meanFC_th3.4"
colnames(df_rsfrmi)[6] <- "meanFC_th3.5"

# Assign df
df_rsfrmi_cag_ctrl <- df_rsfrmi

# Convert var type
df_rsfrmi_cag_ctrl[c(1:2)] <- lapply(df_rsfrmi_cag_ctrl[c(1:2)], as.factor)
df_rsfrmi_cag_ctrl <- as_tibble(df_rsfrmi_cag_ctrl)

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_rsfrmi_cag_ctrl_z <- func_z(df_rsfrmi_cag_ctrl)
df_rsfrmi_cag_ctrl_z <- as_tibble(df_rsfrmi_cag_ctrl_z)
```
# Load and Preprocess FSE LC Data
```{r FSE LC AGBRESA}
# lc
# Read data
df_lc <- read.csv("/Users/astahn/Publications/AGBRESA/Data/LC/LCNE_AGBRESA_semiaut_LCmetaMask_threshold50plus_s01f_complete_mean_zcorr_Multimodal_acrossHem_splitTime.csv", header = TRUE, sep = ",")

# Extract ID
df_lc$ID <- gsub( "^.*ST", "", df_lc$ID ) # delete everything before ST

# Clean
names(df_lc) <- tolower(names(df_lc))
        
# melt to long format
df_lc <- reshape2::melt(df_lc, id.vars = "id") 

# Extract time
df_lc$time.f <- gsub( "^.*0", "", df_lc$variable ) # delete everything before ST

# Relabel
df_lc$time.f <- revalue(df_lc$time.f, c("1"="BDC-3", "2"="HDT30", "3"="HDT59", "4"="R+11"))
df_lc <- df_lc[c(1,4,2,3)]

# clean variable
df_lc$variable <- gsub("\\_mean_.*","", df_lc$variable) # delete everything before .

# Convert var type
df_lc[c(1:3)] <- lapply(df_lc[c(1:3)], as.factor)
df_lc <- as_tibble(df_lc)

# Convert to wide
df_lc <- reshape2::dcast(df_lc, id + time.f ~ variable)

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_lc_z <- func_z(df_lc)
df_lc_z <- as_tibble(df_lc_z)
```
# Load and Preprocess VBM
```{r VBM AGBRESA}
# Read data
df_vbm <- read.csv("/Users/astahn/Publications/AGBRESA/Data/VBM/New_20200608/VBM_CATcross_AGi_c_temporalcortex.csv", header = TRUE, sep = ",")


df_vbm <- read.csv("/Users/astahn/Publications/AGBRESA/Data/VBM/New_20200608/VBM_CATcross_correct_direction!!!_wide_.csv", header = TRUE, sep = ",")

# Drop vars
df_vbm <- df_vbm[-c(2:4)]

# Convert column names to lower case
names(df_vbm) <- tolower(names(df_vbm))

# melt to long
df_vbm <- reshape2::melt(df_vbm, id.vars = c("id"))
df_vbm$time.f <- df_vbm$variable

# Extract time
df_vbm$time.f <- gsub(".*insula.", "", df_vbm$time.f)     


# Extract side
df_vbm$side <- df_vbm$variable
df_vbm$side <- gsub("insula.*", "", df_vbm$side)    
df_vbm$side <- gsub("control_ag_", "", df_vbm$side)    

df_vbm <- df_vbm[-c(2)]

# Relabel time.f
df_vbm$time.f <- revalue(df_vbm$time.f, c("bdc3"="BDC-3", "hdt30"="HDT30", "hdt59"="HDT59", "r11"="R+11"))

# Convert to wide
df_vbm <- reshape2::dcast(df_vbm, id + time.f ~ side, value.var = "value")

# Rename
colnames(df_vbm)[3] <-  "insula_left"
colnames(df_vbm)[4] <-  "insula_right"

# Convert var type
df_vbm[c(1:2)] <- lapply(df_vbm[c(1:2)], as.factor)
df_vbm <- as_tibble(df_vbm)

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_vbm_z <- func_z(df_vbm)
df_vbm_z <- as_tibble(df_vbm_z)
```
# Load and Preprocess AGBRESA HC UPenn
```{r highres HC UPenn AGBRESA}
# AGBRESA
# UPenn
df_hc_ag_pre_post_upenn <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20200119/UPenn_Atlas.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_ag_pre_post_upenn$ID <- gsub(".*ST_(.+)_20.*", "\\1", df_hc_ag_pre_post_upenn$ID)

# Extract time
df_hc_ag_pre_post_upenn$time.f <- df_hc_ag_pre_post_upenn$ID
df_hc_ag_pre_post_upenn$time.f <- gsub( "_2", "", df_hc_ag_pre_post_upenn$time.f )
df_hc_ag_pre_post_upenn$time.f <- gsub(".*_","",df_hc_ag_pre_post_upenn$time.f)
#df_hc_ag_pre_post_upenn$time.f <- gsub( "^*._", "", df_hc_ag_pre_post_upenn$time.f )

# Extract ID
df_hc_ag_pre_post_upenn$ID <- gsub( "_.*$", "", df_hc_ag_pre_post_upenn$ID ) # extract everything after _ from start

# Remove duplicate rows
df_hc_ag_pre_post_upenn <- df_hc_ag_pre_post_upenn %>% distinct()

# Drop incomplete data
df_hc_ag_pre_post_upenn <- subset(df_hc_ag_pre_post_upenn, ID != "S1")

# AGBRESA S1 and RSL  
df_hc_rsl_and_ag_s1_upenn <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/_UPenn_Atlas_newMPI_RSL.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_rsl_and_ag_s1_upenn$ID <- gsub( "-", "_", df_hc_rsl_and_ag_s1_upenn$ID )

# Extract time.f
df_hc_rsl_and_ag_s1_upenn$time.f <- df_hc_rsl_and_ag_s1_upenn$ID
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub('.{7}$', '', df_hc_rsl_and_ag_s1_upenn$time.f) #delete last 11 digits
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub( "2016_", "", df_hc_rsl_and_ag_s1_upenn$time.f )
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub(".*_(.+)_.*", "\\1", df_hc_rsl_and_ag_s1_upenn$time.f)

# Extract ID
df_hc_rsl_and_ag_s1_upenn$ID <- gsub( "_.*$", "", df_hc_rsl_and_ag_s1_upenn$ID )

# Rearrange
df_hc_rsl_and_ag_s1_upenn <- df_hc_rsl_and_ag_s1_upenn[c(1,47,2:46)]

# Relabel time.f
df_hc_rsl_and_ag_s1_upenn$time.f <- revalue(df_hc_rsl_and_ag_s1_upenn$time.f, c("BDC4"="BDC-4", "R12"="R+12", "HDT"="HDT58", "BDC"="BDC-4"))

# Extract RSL
df_hc_rsl_upenn <- subset(df_hc_rsl_and_ag_s1_upenn, ID !="S1")

# Extract S1 AGBRESA
df_hc_ag_s1_upenn <- subset(df_hc_rsl_and_ag_s1_upenn, ID =="S1")

# AGBRESA HDT30 R+11
df_hc_ag_30_R11_upenn <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20200603/_UPenn_Atlas_AGBRESA_HDT30_R+11.csv", header = TRUE, sep = ",")
df_hc_ag_30_R11_upenn <- df_hc_ag_30_R11_upenn[-c(49, 50),] # drop empty rows
colnames(df_hc_ag_30_R11_upenn)[2] <-  "time.f"

# Drop incomplete data
df_hc_ag_30_R11_upenn <- subset(df_hc_ag_30_R11_upenn, ID != "S1")

# Combine dfs
# Drop ICV (missing from AGBRESA HDT30 R+11, and not needed because only corrected data will be used)
df_hc_ag_upenn <- rbind(df_hc_ag_pre_post_upenn[-c(13)], df_hc_ag_s1_upenn[-c(14)])
df_hc_ag_upenn <- rbind(df_hc_ag_upenn, df_hc_ag_30_R11_upenn)
names(df_hc_ag_upenn)

# Rearrange
df_hc_ag_upenn <- df_hc_ag_upenn[c(1,46,2:45)]
df_hc_ag_upenn <- as_tibble(df_hc_ag_upenn)

# Convert data type
df_hc_ag_upenn[c(1:2)] <- lapply(df_hc_ag_upenn[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_ag_upenn) <- tolower(names(df_hc_ag_upenn))

# Clean 
# Delete raw data
df_hc_ag_upenn <- df_hc_ag_upenn[grep("raw", names(df_hc_ag_upenn), value = TRUE, invert = TRUE)]

# Delete raw data upenn_usegray_corr_
names(df_hc_ag_upenn) <- gsub("upenn_usegray_corr_", "", names(df_hc_ag_upenn))

# Calculate bilateral volumes
df_hc_ag_upenn$dg <- df_hc_ag_upenn$dg_left + df_hc_ag_upenn$dg_right
df_hc_ag_upenn$ca1 <- df_hc_ag_upenn$ca1_left + df_hc_ag_upenn$ca1_right
df_hc_ag_upenn$ca2 <- df_hc_ag_upenn$ca2_left + df_hc_ag_upenn$ca2_right
df_hc_ag_upenn$ca3 <- df_hc_ag_upenn$ca3_left + df_hc_ag_upenn$ca3_right
df_hc_ag_upenn$misc <- df_hc_ag_upenn$misc_left + df_hc_ag_upenn$misc_right
df_hc_ag_upenn$sub <- df_hc_ag_upenn$sub_left + df_hc_ag_upenn$sub_right
df_hc_ag_upenn$erc <- df_hc_ag_upenn$erc_left + df_hc_ag_upenn$erc_right
df_hc_ag_upenn$ba35 <- df_hc_ag_upenn$ba35_left + df_hc_ag_upenn$ba35_right
df_hc_ag_upenn$ba36 <- df_hc_ag_upenn$ba36_left + df_hc_ag_upenn$ba36_right
df_hc_ag_upenn$phc <- df_hc_ag_upenn$phc_left + df_hc_ag_upenn$phc_right
df_hc_ag_upenn$sulcus <- df_hc_ag_upenn$sulcus_left + df_hc_ag_upenn$sulcus_right

# Calculate total volume
df_hc_ag_upenn$hc_total <- df_hc_ag_upenn$dg + df_hc_ag_upenn$ca1 + df_hc_ag_upenn$ca2 + df_hc_ag_upenn$ca3 + df_hc_ag_upenn$sub + df_hc_ag_upenn$erc + df_hc_ag_upenn$phc


# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_hc_ag_upenn_z <- func_z(df_hc_ag_upenn)
df_hc_ag_upenn_z <- as_tibble(df_hc_ag_upenn_z)
```
# Load and Preprocess AGBRESA MPI
```{r highres HC MPI AGBRESA}
# AGBRESA
# MPI
df_hc_ag_pre_post_mpi <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20200119/_MPIB_Atlas.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_ag_pre_post_mpi$ID <- gsub(".*ST_(.+)_20.*", "\\1", df_hc_ag_pre_post_mpi$ID)

# Extract time
df_hc_ag_pre_post_mpi$time.f <- df_hc_ag_pre_post_mpi$ID
df_hc_ag_pre_post_mpi$time.f <- gsub( "_2", "", df_hc_ag_pre_post_mpi$time.f )
df_hc_ag_pre_post_mpi$time.f <- gsub(".*_","", df_hc_ag_pre_post_mpi$time.f)

# Extract ID
df_hc_ag_pre_post_mpi$ID <- gsub( "_.*$", "", df_hc_ag_pre_post_mpi$ID ) # extract everything after _ from start

# Remove duplicate rows
df_hc_ag_pre_post_mpi <- df_hc_ag_pre_post_mpi %>% distinct()

# Drop incomplete data
df_hc_ag_pre_post_mpi <- subset(df_hc_ag_pre_post_mpi, ID != "S1")

# AGBRESA MPI S1
df_hc_ag_s1_mpi <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/_MPIB_Atlas_AGBRESA_S1.csv", header = TRUE, sep = ",")

# Extract time.f
df_hc_ag_s1_mpi$time.f <- gsub( "S1_", "", df_hc_ag_s1_mpi$ID )

# Relabel time.f
df_hc_ag_s1_mpi$time.f <- revalue(df_hc_ag_s1_mpi$time.f, c("BDC"="BDC-4"))

# Extract ID
df_hc_ag_s1_mpi$ID <- gsub( "_.*$", "", df_hc_ag_s1_mpi$ID )

# AGBRESA HDT30 R+11
df_hc_ag_30_R11_mpi <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20200603/_MPIB_Atlas_AGBRESA_HDT30_R+11.csv", header = TRUE, sep = ",")
df_hc_ag_30_R11_mpi <- df_hc_ag_30_R11_mpi[-c(49),] # drop empty rows
colnames(df_hc_ag_30_R11_mpi)[2] <-  "time.f"

# Drop incomplete data
df_hc_ag_30_R11_mpi <- subset(df_hc_ag_30_R11_mpi, ID != "S1")

# Combine dfs
# Drop ICV (missing from AGBRESA HDT30 R+11, and not needed because only corrected data will be used)
df_hc_ag_mpi <- rbind(df_hc_ag_pre_post_mpi[-c(6)], df_hc_ag_s1_mpi[-c(6)])
df_hc_ag_mpi <- rbind(df_hc_ag_mpi, df_hc_ag_30_R11_mpi[-c(7)])
names(df_hc_ag_mpi)

# Rearrange
df_hc_ag_mpi <- df_hc_ag_mpi[c(1,18,2:17)]
df_hc_ag_mpi <- as_tibble(df_hc_ag_mpi)

# Convert data type
df_hc_ag_mpi[c(1:2)] <- lapply(df_hc_ag_mpi[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_ag_mpi) <- tolower(names(df_hc_ag_mpi))

# Clean 
# Delete raw data
df_hc_ag_mpi <- df_hc_ag_mpi[grep("raw", names(df_hc_ag_mpi), value = TRUE, invert = TRUE)]

# Delete raw data mpi_usegray_corr_
names(df_hc_ag_mpi) <- gsub("mpib_corr_usegray_", "", names(df_hc_ag_mpi))

# add underline for left and
colnames(df_hc_ag_mpi)[3] <-  "ca1_left"
colnames(df_hc_ag_mpi)[4] <-  "dg_left"
colnames(df_hc_ag_mpi)[5] <-  "sub_left"
colnames(df_hc_ag_mpi)[6] <-  "erc_left"
colnames(df_hc_ag_mpi)[7] <-  "ca1_right"
colnames(df_hc_ag_mpi)[8] <-  "dg_right"
colnames(df_hc_ag_mpi)[9] <-  "sub_right"
colnames(df_hc_ag_mpi)[10] <-  "erc_right"

# Calculate bilateral volumes
df_hc_ag_mpi$dg <- df_hc_ag_mpi$dg_left + df_hc_ag_mpi$dg_right
df_hc_ag_mpi$ca1 <- df_hc_ag_mpi$ca1_left + df_hc_ag_mpi$ca1_right
df_hc_ag_mpi$sub <- df_hc_ag_mpi$sub_left + df_hc_ag_mpi$sub_right
df_hc_ag_mpi$erc <- df_hc_ag_mpi$erc_left + df_hc_ag_mpi$erc_right

# Calculate total volume
df_hc_ag_mpi$hc_total <- df_hc_ag_mpi$dg + df_hc_ag_mpi$ca1 +  + df_hc_ag_mpi$sub + df_hc_ag_mpi$erc 


# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_hc_ag_mpi_z <- func_z(df_hc_ag_mpi)
df_hc_ag_mpi_z <- as_tibble(df_hc_ag_mpi_z)
```
# Load and Preprocess RSL UPenn
```{r highres HC UPenn RSL}
# RSL

# AGBRESA S1 and RSL  
df_hc_rsl_and_ag_s1_upenn <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/_UPenn_Atlas_newMPI_RSL.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_rsl_and_ag_s1_upenn$ID <- gsub( "-", "_", df_hc_rsl_and_ag_s1_upenn$ID )

# Extract time.f
df_hc_rsl_and_ag_s1_upenn$time.f <- df_hc_rsl_and_ag_s1_upenn$ID
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub('.{7}$', '', df_hc_rsl_and_ag_s1_upenn$time.f) #delete last 11 digits
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub( "2016_", "", df_hc_rsl_and_ag_s1_upenn$time.f )
df_hc_rsl_and_ag_s1_upenn$time.f <- gsub(".*_(.+)_.*", "\\1", df_hc_rsl_and_ag_s1_upenn$time.f)

# Extract ID
df_hc_rsl_and_ag_s1_upenn$ID <- gsub( "_.*$", "", df_hc_rsl_and_ag_s1_upenn$ID )

# Rearrange
df_hc_rsl_and_ag_s1_upenn <- df_hc_rsl_and_ag_s1_upenn[c(1,47,2:46)]

# Extract RSL
df_hc_rsl_upenn <- subset(df_hc_rsl_and_ag_s1_upenn, ID !="S1")

# Combine dfs
# Drop ICV (because only corrected data will be used)
df_hc_rsl_upenn <- df_hc_rsl_upenn[-c(14)]

df_hc_rsl_upenn <- as_tibble(df_hc_rsl_upenn)

# Convert data type
df_hc_rsl_upenn[c(1:2)] <- lapply(df_hc_rsl_upenn[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_rsl_upenn) <- tolower(names(df_hc_rsl_upenn))

# Clean 
# Delete raw data
df_hc_rsl_upenn <- df_hc_rsl_upenn[grep("raw", names(df_hc_rsl_upenn), value = TRUE, invert = TRUE)]

# Delete raw data upenn_usegray_corr_
names(df_hc_rsl_upenn) <- gsub("upenn_usegray_corr_", "", names(df_hc_rsl_upenn))

# Calculate bilateral volumes
df_hc_rsl_upenn$dg <- df_hc_rsl_upenn$dg_left + df_hc_rsl_upenn$dg_right
df_hc_rsl_upenn$ca1 <- df_hc_rsl_upenn$ca1_left + df_hc_rsl_upenn$ca1_right
df_hc_rsl_upenn$ca2 <- df_hc_rsl_upenn$ca2_left + df_hc_rsl_upenn$ca2_right
df_hc_rsl_upenn$ca3 <- df_hc_rsl_upenn$ca3_left + df_hc_rsl_upenn$ca3_right
df_hc_rsl_upenn$misc <- df_hc_rsl_upenn$misc_left + df_hc_rsl_upenn$misc_right
df_hc_rsl_upenn$sub <- df_hc_rsl_upenn$sub_left + df_hc_rsl_upenn$sub_right
df_hc_rsl_upenn$erc <- df_hc_rsl_upenn$erc_left + df_hc_rsl_upenn$erc_right
df_hc_rsl_upenn$ba35 <- df_hc_rsl_upenn$ba35_left + df_hc_rsl_upenn$ba35_right
df_hc_rsl_upenn$ba36 <- df_hc_rsl_upenn$ba36_left + df_hc_rsl_upenn$ba36_right
df_hc_rsl_upenn$phc <- df_hc_rsl_upenn$phc_left + df_hc_rsl_upenn$phc_right
df_hc_rsl_upenn$sulcus <- df_hc_rsl_upenn$sulcus_left + df_hc_rsl_upenn$sulcus_right

# Calculate total volume
df_hc_rsl_upenn$hc_total <- df_hc_rsl_upenn$dg + df_hc_rsl_upenn$ca1 + df_hc_rsl_upenn$ca2 + df_hc_rsl_upenn$ca3 + df_hc_rsl_upenn$sub + df_hc_rsl_upenn$erc + df_hc_rsl_upenn$phc

# Relabel time.f
df_hc_rsl_upenn$time.f <- revalue(df_hc_rsl_upenn$time.f, c("BDC4"="BDC-4", "R12"="R+12", "HDT"="HDT58", "BDC"="BDC-4"))

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-4" )

# Run z scores
df_hc_rsl_upenn_z <- func_z(df_hc_rsl_upenn)
df_hc_rsl_upenn_z <- as_tibble(df_hc_rsl_upenn_z)
```
# Load and Preprocess RSL MPI
```{r highres HC MPI RSL}
# RSL
df_hc_rsl_mpi <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/MPIB_Atlas_RSL.csv", header = TRUE, sep = ",")

df_hc_rsl_mpi <- df_hc_rsl_mpi[-c(116),] # drop empty rows

# Clean ID
df_hc_rsl_mpi$ID <- gsub("-","_", df_hc_rsl_mpi$ID)


# Extract time.f
df_hc_rsl_mpi$time.f <- gsub('.{8}$', '', df_hc_rsl_mpi$ID) #delete last 11 digits
df_hc_rsl_mpi$time.f <- gsub(".*_(.+)_.*", "\\1", df_hc_rsl_mpi$time.f)

# Extract ID
df_hc_rsl_mpi$ID <- gsub( "_.*$", "", df_hc_rsl_mpi$ID )

# Remove duplicate rows
df_hc_rsl_mpi <- df_hc_rsl_mpi %>% distinct()

# Reorder
names(df_hc_rsl_mpi)
df_hc_rsl_mpi <- df_hc_rsl_mpi[c(1, 19, 2:18)]

# Drop ICV (missing from AGBRESA HDT30 R+11, and not needed because only corrected data will be used)
df_hc_rsl_mpi <-df_hc_rsl_mpi[-c(7)]

df_hc_rsl_mpi <- as_tibble(df_hc_rsl_mpi)

# Convert data type
df_hc_rsl_mpi[c(1:2)] <- lapply(df_hc_rsl_mpi[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_rsl_mpi) <- tolower(names(df_hc_rsl_mpi))

# Clean 
# Delete raw data
df_hc_rsl_mpi <- df_hc_rsl_mpi[grep("raw", names(df_hc_rsl_mpi), value = TRUE, invert = TRUE)]

# Delete raw data mpi_usegray_corr_
names(df_hc_rsl_mpi) <- gsub("mpib_corr_usegray_", "", names(df_hc_rsl_mpi))

# add underline for left and
colnames(df_hc_rsl_mpi)[3] <-  "ca1_left"
colnames(df_hc_rsl_mpi)[4] <-  "dg_left"
colnames(df_hc_rsl_mpi)[5] <-  "sub_left"
colnames(df_hc_rsl_mpi)[6] <-  "erc_left"
colnames(df_hc_rsl_mpi)[7] <-  "ca1_right"
colnames(df_hc_rsl_mpi)[8] <-  "dg_right"
colnames(df_hc_rsl_mpi)[9] <-  "sub_right"
colnames(df_hc_rsl_mpi)[10] <-  "erc_right"

# Calculate bilateral volumes
df_hc_rsl_mpi$dg <- df_hc_rsl_mpi$dg_left + df_hc_rsl_mpi$dg_right
df_hc_rsl_mpi$ca1 <- df_hc_rsl_mpi$ca1_left + df_hc_rsl_mpi$ca1_right
df_hc_rsl_mpi$sub <- df_hc_rsl_mpi$sub_left + df_hc_rsl_mpi$sub_right
df_hc_rsl_mpi$erc <- df_hc_rsl_mpi$erc_left + df_hc_rsl_mpi$erc_right

# Calculate total volume
df_hc_rsl_mpi$hc_total <- df_hc_rsl_mpi$dg + df_hc_rsl_mpi$ca1 +  + df_hc_rsl_mpi$sub + df_hc_rsl_mpi$erc 

# Relabel time.f
df_hc_rsl_mpi$time.f <- revalue(df_hc_rsl_mpi$time.f, c("BDC4"="BDC-4", "R12"="R+12", "HDT"="HDT58", "BDC"="BDC-4"))

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-4" )

# Run z scores
df_hc_rsl_mpi_z <- func_z(df_hc_rsl_mpi)
df_hc_rsl_mpi_z <- as_tibble(df_hc_rsl_mpi_z)
```
# Load and Preprocess Cocktail UPenn
```{r highres HC UPenn Cocktail}
# Cocktail
df_hc_cocktail_upenn <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/_UPenn_Atlas_Cocktail.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_cocktail_upenn$ID <- gsub( "-", "_", df_hc_cocktail_upenn$ID )
df_hc_cocktail_upenn$ID <-gsub('.{14}$', '', df_hc_cocktail_upenn$ID) #delete last 11 digits

# Extract time.f
df_hc_cocktail_upenn$time.f <- gsub( "_.*$", "", df_hc_cocktail_upenn$ID ) # extract everything after _ from start

# Extract id
df_hc_cocktail_upenn$ID <- gsub('BDC5_', '', df_hc_cocktail_upenn$ID) 
df_hc_cocktail_upenn$ID <- gsub('HDT57_', '', df_hc_cocktail_upenn$ID) 
df_hc_cocktail_upenn$ID  <- gsub( "_.*$", "", df_hc_cocktail_upenn$ID  ) # extract everything after _ from start

# Drop ICV (because only corrected data will be used)
df_hc_cocktail_upenn <- df_hc_cocktail_upenn[-c(13)]

# Reorder
names(df_hc_cocktail_upenn)
df_hc_cocktail_upenn <- df_hc_cocktail_upenn[c(1, 46, 2:45)]

df_hc_cocktail_upenn <- as_tibble(df_hc_cocktail_upenn)

# Convert data type
df_hc_cocktail_upenn[c(1:2)] <- lapply(df_hc_cocktail_upenn[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_cocktail_upenn) <- tolower(names(df_hc_cocktail_upenn))

# Clean 
# Delete raw data
df_hc_cocktail_upenn <- df_hc_cocktail_upenn[grep("raw", names(df_hc_cocktail_upenn), value = TRUE, invert = TRUE)]

# Delete raw data upenn_usegray_corr_
names(df_hc_cocktail_upenn) <- gsub("upenn_usegray_corr_", "", names(df_hc_cocktail_upenn))

# Calculate bilateral volumes
df_hc_cocktail_upenn$dg <- df_hc_cocktail_upenn$dg_left + df_hc_cocktail_upenn$dg_right
df_hc_cocktail_upenn$ca1 <- df_hc_cocktail_upenn$ca1_left + df_hc_cocktail_upenn$ca1_right
df_hc_cocktail_upenn$ca2 <- df_hc_cocktail_upenn$ca2_left + df_hc_cocktail_upenn$ca2_right
df_hc_cocktail_upenn$ca3 <- df_hc_cocktail_upenn$ca3_left + df_hc_cocktail_upenn$ca3_right
df_hc_cocktail_upenn$misc <- df_hc_cocktail_upenn$misc_left + df_hc_cocktail_upenn$misc_right
df_hc_cocktail_upenn$sub <- df_hc_cocktail_upenn$sub_left + df_hc_cocktail_upenn$sub_right
df_hc_cocktail_upenn$erc <- df_hc_cocktail_upenn$erc_left + df_hc_cocktail_upenn$erc_right
df_hc_cocktail_upenn$ba35 <- df_hc_cocktail_upenn$ba35_left + df_hc_cocktail_upenn$ba35_right
df_hc_cocktail_upenn$ba36 <- df_hc_cocktail_upenn$ba36_left + df_hc_cocktail_upenn$ba36_right
df_hc_cocktail_upenn$phc <- df_hc_cocktail_upenn$phc_left + df_hc_cocktail_upenn$phc_right
df_hc_cocktail_upenn$sulcus <- df_hc_cocktail_upenn$sulcus_left + df_hc_cocktail_upenn$sulcus_right

# Calculate total volume
df_hc_cocktail_upenn$hc_total <- df_hc_cocktail_upenn$dg + df_hc_cocktail_upenn$ca1 + df_hc_cocktail_upenn$ca2 + df_hc_cocktail_upenn$ca3 + df_hc_cocktail_upenn$sub + df_hc_cocktail_upenn$erc + df_hc_cocktail_upenn$phc

# Relabel time.f
df_hc_cocktail_upenn$time.f <- revalue(df_hc_cocktail_upenn$time.f, c("BDC5"="BDC-5", "HDT57"="HDT57"))

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-5" )

# Run z scores
df_hc_cocktail_upenn_z <- func_z(df_hc_cocktail_upenn)
df_hc_cocktail_upenn_z <- as_tibble(df_hc_cocktail_upenn_z)
```
# Load and Preprocess Cocktail MPI
```{r highres HC MPI Cocktail}
# Cocktail
df_hc_cocktail_mpi <- read.csv("/Users/astahn/Publications/AGBRESA/Data/High Res HC/20201208/_MPIB_Atlas_Cocktail.csv", header = TRUE, sep = ",")

# Clean ID
df_hc_cocktail_mpi$ID <- gsub( "-", "_", df_hc_cocktail_mpi$ID )
df_hc_cocktail_mpi$ID <-gsub('.{14}$', '', df_hc_cocktail_mpi$ID) #delete last 11 digits

# Extract time.f
df_hc_cocktail_mpi$time.f <- gsub( "_.*$", "", df_hc_cocktail_mpi$ID ) # extract everything after _ from start

# Extract id
df_hc_cocktail_mpi$ID <- gsub('BDC5_', '', df_hc_cocktail_mpi$ID) 
df_hc_cocktail_mpi$ID <- gsub('HDT57_', '', df_hc_cocktail_mpi$ID) 
df_hc_cocktail_mpi$ID  <- gsub( "_.*$", "", df_hc_cocktail_mpi$ID  ) # extract everything after _ from start


# Drop ICV (because only corrected data will be used)
df_hc_cocktail_mpi <- df_hc_cocktail_mpi[-c(6)]

# Reorder
names(df_hc_cocktail_upenn)
df_hc_cocktail_mpi <- df_hc_cocktail_mpi[c(1, 18, 2:17)]

df_hc_cocktail_mpi <- as_tibble(df_hc_cocktail_mpi)

# Convert data type
df_hc_cocktail_mpi[c(1:2)] <- lapply(df_hc_cocktail_mpi[c(1:2)], as.factor)

# Clean vars
# Convert column names to lower case
names(df_hc_cocktail_mpi) <- tolower(names(df_hc_cocktail_mpi))

# Clean 
# Delete raw data
df_hc_cocktail_mpi <- df_hc_cocktail_mpi[grep("raw", names(df_hc_cocktail_mpi), value = TRUE, invert = TRUE)]

# Delete raw data upenn_usegray_corr_
names(df_hc_cocktail_mpi) <- gsub("mpib_corr_usegray_", "", names(df_hc_cocktail_mpi))

# add underline for left and
colnames(df_hc_cocktail_mpi)[3] <-  "ca1_left"
colnames(df_hc_cocktail_mpi)[4] <-  "dg_left"
colnames(df_hc_cocktail_mpi)[5] <-  "sub_left"
colnames(df_hc_cocktail_mpi)[6] <-  "erc_left"
colnames(df_hc_cocktail_mpi)[7] <-  "ca1_right"
colnames(df_hc_cocktail_mpi)[8] <-  "dg_right"
colnames(df_hc_cocktail_mpi)[9] <-  "sub_right"
colnames(df_hc_cocktail_mpi)[10] <-  "erc_right"

# Calculate bilateral volumes
df_hc_cocktail_mpi$dg <- df_hc_cocktail_mpi$dg_left + df_hc_cocktail_mpi$dg_right
df_hc_cocktail_mpi$ca1 <- df_hc_cocktail_mpi$ca1_left + df_hc_cocktail_mpi$ca1_right
df_hc_cocktail_mpi$sub <- df_hc_cocktail_mpi$sub_left + df_hc_cocktail_mpi$sub_right
df_hc_cocktail_mpi$erc <- df_hc_cocktail_mpi$erc_left + df_hc_cocktail_mpi$erc_right

# Calculate total volume
df_hc_cocktail_mpi$hc_total <- df_hc_cocktail_mpi$dg + df_hc_cocktail_mpi$ca1 +  + df_hc_cocktail_mpi$sub + df_hc_cocktail_mpi$erc 

# Relabel time.f
df_hc_cocktail_mpi$time.f <- revalue(df_hc_cocktail_mpi$time.f, c("BDC5"="BDC-5", "HDT"="HDT57"))

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-5" )

# Run z scores
df_hc_cocktail_mpi_z <- func_z(df_hc_cocktail_mpi)
df_hc_cocktail_mpi_z <- as_tibble(df_hc_cocktail_mpi_z)
```
# Load and Preprocess MTR Data
```{r mtr AGBRESA}
# mtr
# Read data
df_mtr <- read.csv("/Users/astahn/Publications/AGBRESA/Data/MTR/MT_ROis_ed.csv",header = TRUE, sep = ",")

# Convert var type
df_mtr[c(1:2)] <- lapply(df_mtr[c(1:2)], as.factor)
df_mtr <- as_tibble(df_mtr)

# Define id vars for long format, and bdc data
id_vars <- c("id", "time.f")
bdc <- quote( time.f == "BDC-3" )

# Run z scores
df_mtr_z <- func_z(df_mtr)
df_mtr_z <- as_tibble(df_mtr_z)
```
# Save data
```{r export data}

list_of_datasets <- list(   "rsfrmi AGvCTRL_BDC_HDT59" = df_rsfrmi_ag_ctrl,
                            "rsfrmi cAGvsCTRL_BDC_HDT59" = df_rsfrmi_cag_ctrl,
                            "rsfrmi AGvCTRL_BDC_HDT59 z" = df_rsfrmi_ag_ctrl_z,
                            "rsfrmi cAGvsCTRL_BDC_HDT59 z" = df_rsfrmi_cag_ctrl_z,
                            "VBM" = df_vbm,
                            "VBM z scores" = df_vbm_z,
                            "High Res LC" = df_lc,
                            "High Res LC z" = df_lc_z,
                            "MTR" = df_mtr,
                            "MTR z scores" = df_mtr_z,
                            "HC UPenn" = df_hc_ag_upenn,
                            "HC UPenn z" = df_hc_ag_upenn_z,
                            "HC MPI" = df_hc_ag_mpi,
                            "HC MPI z" = df_hc_ag_mpi_z)

write.xlsx(list_of_datasets, file = "./Data/Data MRI.xlsx", overwrite = TRUE)

list_of_datasets_hc <- list("AGBRESA UPenn HC" = df_hc_ag_upenn,
                            "AGBRESA UPenn HC z" = df_hc_ag_upenn_z,
                            "AGBRESA MPI HC" = df_hc_ag_mpi,
                            "AGBRESA MPI HC z" = df_hc_ag_mpi_z,
                            "RSL MPI HC" = df_hc_cocktail_mpi,
                            "RSL MPI HC z" = df_hc_rsl_mpi_z,
                            "RSL UPenn HC" = df_hc_rsl_upenn,
                            "RSL UPenn HC z" = df_hc_rsl_upenn_z,
                            "Cocktail MPI HC" = df_hc_cocktail_mpi,
                            "Cocktail MPI HC z" = df_hc_cocktail_mpi_z,
                            "Cocktail UPenn HC" = df_hc_cocktail_upenn,
                            "Cocktail UPenn HC z" = df_hc_cocktail_upenn_z)

write.xlsx(list_of_datasets, file = "./Data/Data HC All Bed Rest Studies.xlsx", overwrite = TRUE)                          
```
